---
title: "Analysis_04_Organophosphate_Fish"
author: "Alex Dhond"
date: "7/14/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Introduction

The purpose of this script is to analyze the ORGANOPHOSPHATE data set with FISH ONLY. The script will:

1. Extract the species located in the first quartile of the data; this information will be useful in terms of plotting.
2. Build single-chemical SSDs and extract the true HC5 values
3. Using the leave-one-out approach, build single-chemical SSDs and extract HC5s along with variance estimates.
4. Using all possible combinations of chemicals, create multiple SSDns with multiple nSpecies to get estimates of HC5 values
5. Summarize results generated and prepare plots
6. Plot relevant data

### Clear the existing workspace
```{r}
# Clear existing workspace
rm(list = ls())
```

### Load in required packages
```{r}
library(dplyr) # Used for data manipulation
library(tidyr) # data manipulation
library(RcppAlgos) # Used to create random draws of chemicals
library(data.table) # Used for creating data tables
library(EnvStats) # Used for calculating geometric means
library(plotrix) # used for calculating standard error
library(fitdistrplus) # for fitting various distributions to the data
library(flexsurv) # for fitting parametric distributions
library(ggplot2) # for plotting
library(ggpubr) # for exporting plots
```

### Load in the source data
Load in WEB-ICE data, prefiltered for only chemicals with data for 8+ species
```{r}
# Read in the WEB ICE data
data <- read.csv("https://raw.githubusercontent.com/glted-mib/SSDn-Code/main/ICE_data_8_species.csv")
```

### Filter the data to only include organophosphate chemicals and fish species
```{r}
# Filter to only include organophosphate chemicals 
data <- data %>%
  filter(
    Specific_MOA == "Organophosphate"
  )

# Filter to only include fish species
data <- data %>%
  filter(
    Taxa == "Fish"
  )

# Check how many chemicals we have
unique(data$Chemical)
```

# Check the organophosphate data to see which chemicals have the most fish species and which do not
```{r}
# Filter and summarize the OP data to see which chemicals have the most species
species_summary <- data %>% 
  dplyr::group_by(Chemical) %>% # group by chemical
  summarise(
    number_species = n_distinct(Species)) %>% # calculate number of species
  arrange(desc(number_species)) # arrange in descending order (most species at top)

# Looking at this data, there are 13 chemicals with at least 8 different fish species.

# select the chems that have 8 or more fish and make a vector to filter the main data by
chems_w_8_plus <- species_summary %>%
  filter(number_species >= 8) %>%
  dplyr::select(Chemical) 

# Make it a vector
chems_8_plus_vector <- chems_w_8_plus$Chemical


# Filter the main dataset to only include these chemicals
data <- data %>%
  filter(
    Chemical %in% chems_8_plus_vector
  )

# So, the "chems_8_plus_vector" represents the organophosphate chemicals that have data for 8 or more FISH species only.
```


### Extract relevant information for supplementary tables
How many species are there per chemical, what are range of toxicity values, etc.
```{r}
# Minimum tox value for overall dataset
min(data$Conc) 

# Maximum tox value for overall dataset
max(data$Conc)

### Azinphos-methyl
# How many species are there per chemical?
print(paste("There are", length(unique(data$Species[data$Chemical == "Azinphos-methyl"])), "species in Azinphos-methyl"))

### Chlorpyrifos
# How many species are there per chemical?
print(paste("There are", length(unique(data$Species[data$Chemical == "Chlorpyrifos"])), "species in Chlorpyrifos"))

### Coumaphos
# How many species are there per chemical?
print(paste("There are", length(unique(data$Species[data$Chemical == "Coumaphos"])), "species in Coumaphos"))

### Diazinon
# How many species are there per chemical?
print(paste("There are", length(unique(data$Species[data$Chemical == "Diazinon"])), "species in Diazinon"))

### Dichlorvos
# How many species are there per chemical?
print(paste("There are", length(unique(data$Species[data$Chemical == "Dichlorvos"])), "species in Dichlorvos"))

### Disulfoton
# How many species are there per chemical?
print(paste("There are", length(unique(data$Species[data$Chemical == "Disulfoton"])), "species in Disulfoton"))

### EPN
# How many species are there per chemical?
print(paste("There are", length(unique(data$Species[data$Chemical == "EPN"])), "species in EPN"))

### Fenitrothion
# How many species are there per chemical?
print(paste("There are", length(unique(data$Species[data$Chemical == "Fenitrothion"])), "species in Fenitrothion"))

### Fenthion
# How many species are there per chemical?
print(paste("There are", length(unique(data$Species[data$Chemical == "Fenthion"])), "species in Fenthion"))

### Malathion
# How many species are there per chemical?
print(paste("There are", length(unique(data$Species[data$Chemical == "Malathion"])), "species in Malathion"))

### Methyl parathion
# How many species are there per chemical?
print(paste("There are", length(unique(data$Species[data$Chemical == "Methyl parathion"])), "species in Methyl parathion"))

### Parathion
# How many species are there per chemical?
print(paste("There are", length(unique(data$Species[data$Chemical == "Parathion"])), "species in Parathion"))

### Trichlorfon
# How many species are there per chemical?
print(paste("There are", length(unique(data$Species[data$Chemical == "Trichlorfon"])), "species in Trichlorfon"))
```


# 1. Extract species data for first quartile

Extracting which species are in the first quartile (ie most sensitive species) for all chemicals is useful for making plots at the end.

### Find the species in the first quartile
The variable "all.chem.OP" represents the 13 organophosphate chemicals we will be using for this analysis.
```{r}
# Create a list of organophosphates
all.chem.OP <- c("Azinphos-methyl", "Chlorpyrifos", "Coumaphos", "Diazinon", "Dichlorvos", "Disulfoton", "EPN", "Fenitrothion", "Fenthion", "Malathion", "Methyl parathion", "Parathion", "Trichlorfon")

# Create an empty list for the most sensitive species
most.sensitive.species <- list()

# Create a loop to iterate through all the chemicals in the set
for(i in all.chem.OP) {

  #Calculating the average toxicity value (LC50) for each species 
  IndividualSSDs <- data %>% 
    filter(Chemical == i) %>%
    group_by(Species) %>%
    summarise(
      average = geoMean(Conc), # here I am using "average" instead of "geomean" as earlier
      minimum = min(Conc),
      sd = sd(Conc),
      n = n())
  
  IndividualSSDs <- unique(IndividualSSDs) #Adding toxicity data for each chemical to a list and making sure there are no duplicates
  
  # Create intermediate data frame
  Newdf <- IndividualSSDs
  
  #Calculating the probability points for each species and order them
  df <- Newdf[order(Newdf$average),]
  df$frac <- ppoints(df$average, 0.5)
  
  # Create intermediate data frame and filter by the lowest quartile
  most.sensitive.sp <- df %>%
  filter(
    average <= quantile(df$average, probs = 0.25))
  
  # Combine the data for this chemical into a data frame
  most.sensitive.sp.table <- data.frame(i, most.sensitive.sp)
  
  # Save this run of the loop as a place in the list
  most.sensitive.species[[i]] <- most.sensitive.sp.table
}

# Bind all of the elements of the list together into one data frame
most.sensitive.species <- rbindlist(most.sensitive.species)

# Rename the column names
colnames(most.sensitive.species) <- c("Chemical", "Species", "average", "minimum", "sd", "n", "frac")
```

# 2. Build single-chemical SSDs and extract HC5 values
We need to get the "true" HC5 values from the single chemical SSDs. The following code builds the single chemical SSDs and extracts the HC5 values from them.

### Extracting HC5 values for single chemicals
```{r}
# Create a list of chemicals from my data set
single.ssd.chems <- unique(data$Chemical)

# The individual.hc5s list will contain HC5 values from chemical-specific SSDs built using the best-fit method. These HC5s will be compared to the HC5s derived from SSDns.
individual.hc5s <- list()

#This loop calculates HC5 values from chemical-specific SSDs for each chemical in the all.chems list. It uses the best-fit method to fit the most appropriate distribution to individual chemical toxicity data (out of log-normal, log-logisitc, Weibull, and gamma distributions). The Anderson-Darling statistic is used to determine best-fit. The distribution with the lowest Anderson-Darling statistic is assigned as the "best.fit" method.
for(i in single.ssd.chems) {
  
  fit_gamma <- NULL
  best.fit <- NULL
  
  #Calculating the average toxicity value (LC50) for each species 
  IndividualSSDs <- data %>% filter(Chemical == i) %>%
    group_by(Species) %>%
    summarise(
      average = geoMean(Conc), # here I am using "average" instead of "geomean" as earlier
      minimum = min(Conc),
      sd = sd(Conc),
      n = n())
  
  IndividualSSDs <- unique(IndividualSSDs) #Adding toxicity data for each chemical to a list and making sure there are no duplicates
  
  # Create intermediate data frame
  Newdf <- IndividualSSDs
  
  #Calculating the probability points for each species 
  df <- Newdf[order(Newdf$average),]
  df$frac <- ppoints(df$average, 0.5)
  df
  
  #Fit a distribution to the plotted points
  fit_llogis <- fitdist(df$average, "llogis")
  fit_lnorm <- fitdist(df$average, "lnorm")
  fit_gamma <- try(fitdist(df$average, "gamma"), silent = TRUE) # use try here as gamma often fails
  fit_weibull <- fitdist(df$average, "weibull")
  
  # if there is an error with the gamma distribution, fit the other three instead
  if("try-error" %in% class(fit_gamma)){
    ll <- gofstat(fit_llogis)
    ln <- gofstat(fit_lnorm)
    w <- gofstat(fit_weibull)
    
    #Fit the best distribution to the data; identify it by the lowest anderson darling statistic
    a <- unlist(c(ll[8], ln[8], w[8]))
    best.fit.table <- data.table(c("llogis", "lnorm", "weibull"), a)
    m <- min(a)
    b <- best.fit.table$V1[best.fit.table$a == m]
  }  else {
    ll <- gofstat(fit_llogis)
    ln <- gofstat(fit_lnorm)
    g <- gofstat(fit_gamma)
    w <- gofstat(fit_weibull)
    
    #Fit the best distribution to the data; identify it by the lowest anderson darling statistic
    a <- unlist(c(ll[8], ln[8], g[8], w[8]))
    best.fit.table <- data.table(c("llogis", "lnorm", "gamma", "weibull"), a)
    m <- min(a)
    b <- best.fit.table$V1[best.fit.table$a == m]}
  
  #Calculate the best fit distribution
  best.fit <- fitdist(df$average, b)
  
  # Extract the estimated HC5 value
  hc5 <- quantile(best.fit, probs = 0.05)
  Estimated_HC5 <- hc5$quantiles$`p=0.05`
  
  # Bootstrap the HC5 value with upper and lower CIs
  fit_boot <- bootdist(best.fit, bootmethod = 'param', niter = 1000)
  
  # This step is not necessary I am just using it to check the bootstrap is working
  bootstrap_hc5 <- quantile(fit_boot, probs = 0.05)
  
  # Save the bootstrap and upper and lower confidence intervals
  Bootstrapped_HC5 <- bootstrap_hc5$quantiles$`p=0.05`
  HC5_lower_ci <- bootstrap_hc5$quantCI[1,1]
  HC5_upper_ci <- bootstrap_hc5$quantCI[2,1]
  
  # Save the HC5 values
  hc5.table <- data.frame(i, Estimated_HC5, Bootstrapped_HC5, HC5_lower_ci, HC5_upper_ci, b, m)
  
  individual.hc5s[[i]] <- hc5.table
}

#Binding the list of individual SSD hc5 values together 
individual.hc5s <- rbindlist(individual.hc5s)
colnames(individual.hc5s) <- c("Chemical", "SSD Estimated HC5", "SSD Bootstrapped HC5", "HC5 Lower CI", "HC5 Upper CI", "SSD Dist.", "SSD AD")

# Save the single-chemical HC5s as their own dataframe
single.individual.HC5s <- individual.hc5s
```


We have calculated the single-chemical HC5s, which are a good baseline and represent the "classic" SSD approach. Now, I will use the leave-one-out (LOO) approach to calculate the HC5s along with variance estimates.

# 3. Build and calculate LOO single-chemical SSDs and extract HC5 values.
The LOO approach we decided to use was to first make an SSD with the maximum possible number of species (N). Then, remove one species from the dataset so that the total number of species is (N-1). Using the dataset of (N-1) species, we make another SSD. We would continue to do that until all possible combinations of (N-1) species have been used to make an SSD.

In short, if there were N total species in the original chemical data, then the total number of single-chemical SSDs we could make using this method are N (N possible combinations of N-1 species)

### LOO Loop Generation
NOTE: The warning/error messages it may give are only because the code fits all four distributions (and most of the time, the gamma distribution gives an error). The code fits the best-fit distribution (which does not show an error code)
```{r}
# Create a list of chemicals from my data set
single.ssd.chems <- c("Azinphos-methyl", "Chlorpyrifos", "Coumaphos", "Diazinon", "Dichlorvos", "Disulfoton", "EPN", "Fenitrothion", "Fenthion", "Malathion", "Methyl parathion", "Parathion", "Trichlorfon")

# Initialize the lists that will hold the outputs for the chemicals
individual.hc5s.for.chem <- list()
individual.hc5s <- list()

# Create the loop (it is very similar to creating a normal SSD)
for(i in single.ssd.chems) {
  
  #filter by the chemical
  IndividualSSDs <- data %>% 
    filter(Chemical == i)
  
  # get a list of species and store the length as a variable
  species.list <- unique(IndividualSSDs$Species)
  species.list.length <- length(species.list)

  # create all possible species combinations (such that there are N combinations of N-1 species)
  species.combinations <- list(
  data.table(comboSample(species.list, m = (species.list.length-1), n = species.list.length, repetition = FALSE)))

  # bind all the species combos together
  species.combos.data <- rbindlist(species.combinations)
  
  # initialize a list to hold the species 
  overall.sp.list <- list()
  
  # iterate through and create a species list
  for (j in 1:(length(species.combos.data)+1)){
  # Take the current row (j) and save it as a character vector into a list  
    current.sp.list <- as.character(species.combos.data[j,])
    overall.sp.list[[j]] <- current.sp.list
  }
  
  # Initialize the iterating through sp combinations list
  for (k in 1:length(overall.sp.list)){
  
  # Empty variables for storing output
  fit_gamma <- NULL
  best.fit <- NULL
  
  # Index the current list of species
  current.sp.list <- overall.sp.list[[k]]
  
  # Filter the chemical SSD data by the species that match
  chemical.sp.data <- IndividualSSDs %>%
    filter(Species %in% current.sp.list)
  
  # Filter the species that are left out and save into the data
  sp.left.out <- IndividualSSDs %>%
    dplyr::select(Species) %>%
    filter(!Species %in% chemical.sp.data$Species)
  sp.left.out <- sp.left.out[1,1]
  output.list <- chemical.sp.data
  output.list$Sp.left.out <- sp.left.out

  # Calculate the geomeans and metrics needed to create the SSD (same as single-chemical SSD)
  IndividualSSDs.2 <- output.list %>%
    group_by(Species) %>%
    summarise(
      average = geoMean(Conc), 
      minimum = min(Conc),
      sd = sd(Conc),
      n = n(),
      Chemical = Chemical,
      Sp.left.out = Sp.left.out)

  
  IndividualSSDs.2 <- unique(IndividualSSDs.2) #Adding toxicity data for each chemical to a list and making sure there are no duplicates
  
  # Create intermediate data frame
  Newdf <- IndividualSSDs.2
  
  #Calculating the probability points for each species 
  df <- Newdf[order(Newdf$average),]
  df$frac <- ppoints(df$average, 0.5)
  df
  
   
  #Fit a distribution to the plotted points - there might be errors here so have built in de-bugging
  fit_llogis <- try(fitdist(df$average, "llogis"), silent = TRUE) # there might be an error, see if there is
  fit_lnorm <- try(fitdist(df$average, "lnorm"), silent = TRUE) # there might be an error, see if there is
  fit_gamma <- try(fitdist(df$average, "gamma"), silent = TRUE) # there might be an error, see if there is
  fit_weibull <- try(fitdist(df$average, "weibull"), silent = TRUE) # there might be an error, see if there is

  # If there is an error in all 4 cases, return that there is an error.
  if("try-error" %in% class(fit_gamma) & "try-error" %in% class(fit_llogis) & "try-error" %in% class(fit_weibull) & "try-error" %in% class(fit_lnorm)){
    
    # Paste that there is an error with all 4
    paste("there is an error with all 4 distributions")

  } else if ("try-error" %in% class(fit_gamma) & "try-error" %in% class(fit_llogis) & "try-error" %in% class(fit_weibull)){
    
    # If there is error with gamma, llogis, and weibull, only do lognormal
    ln <- gofstat(fit_lnorm)
    #Fit the best distribution to the data; identify it by the lowest anderson darling statistic
    a <- unlist(c(ln[8]))
    best.fit.table <- data.table(c("lnorm"), a)
    m <- min(a)
    b <- best.fit.table$V1[best.fit.table$a == m]
    
  } else if ("try-error" %in% class(fit_gamma) & "try-error" %in% class(fit_llogis) & "try-error" %in% class(fit_lnorm)){
    
    # If there is error with gamma, llogis, and lnorm, only do weibull
    w <- gofstat(fit_weibull)
    #Fit the best distribution to the data; identify it by the lowest anderson darling statistic
    a <- unlist(c(w[8]))
    best.fit.table <- data.table(c("weibull"), a)
    m <- min(a)
    b <- best.fit.table$V1[best.fit.table$a == m]
    
  } else if ("try-error" %in% class(fit_gamma) & "try-error" %in% class(fit_weibull) & "try-error" %in% class(fit_lnorm)){
    
    # If there is error with gamma, weibull, and lnorm, only do llogis
    ll <- gofstat(fit_llogis)
    #Fit the best distribution to the data; identify it by the lowest anderson darling statistic
    a <- unlist(c(ll[8]))
    best.fit.table <- data.table(c("llogis"), a)
    m <- min(a)
    b <- best.fit.table$V1[best.fit.table$a == m]
    
  } else if ("try-error" %in% class(fit_llogis) & "try-error" %in% class(fit_weibull) & "try-error" %in% class(fit_lnorm)){
    
    # If there is error with llogis, weibull, and lnorm, only do gamma
    g <- gofstat(fit_gamma)
    #Fit the best distribution to the data; identify it by the lowest anderson darling statistic
    a <- unlist(c(g[8]))
    best.fit.table <- data.table(c("gamma"), a)
    m <- min(a)
    b <- best.fit.table$V1[best.fit.table$a == m]
    
  } else if ("try-error" %in% class(fit_gamma) & "try-error" %in% class(fit_llogis)){
    
    # if error with gamma and llogis, try lnorm first
    ln <- gofstat(fit_lnorm)
    
    # try to also fit weibull
    w <- try(gofstat(fit_weibull), silent = TRUE)
    if ("try-error" %in% class(w)){
      
      #only do lnorm
      ln <- gofstat(fit_lnorm)
      # fit distribution to data
      a <- unlist(c(ln[8]))
      best.fit.table <- data.table(c("lnorm"), a)
      m <- min(a)
      b <- best.fit.table$V1[best.fit.table$a == m]
    }
    
    #Fit the best distribution to the data; identify it by the lowest anderson darling statistic
    a <- unlist(c(ln[8], w[8]))
    best.fit.table <- data.table(c("lnorm", "weibull"), a)
    m <- min(a)
    b <- best.fit.table$V1[best.fit.table$a == m]
    
  } else if ("try-error" %in% class(fit_gamma) & "try-error" %in% class(fit_weibull)){
    
    # if error with gamma and weibull, try lnorm first
    ln <- gofstat(fit_lnorm)
    
    # try to also fit llogis
    ll <- try(gofstat(fit_llogis), silent = TRUE)
    if ("try-error" %in% class(ll)){
      #only do lnorm
      ln <- gofstat(fit_lnorm)
      # fit distribution to data
      a <- unlist(c(ln[8]))
      best.fit.table <- data.table(c("lnorm"), a)
      m <- min(a)
      b <- best.fit.table$V1[best.fit.table$a == m]
    }
    
    #Fit the best distribution to the data; identify it by the lowest anderson darling statistic
    a <- unlist(c(ln[8], ll[8]))
    best.fit.table <- data.table(c("lnorm", "llogis"), a)
    m <- min(a)
    b <- best.fit.table$V1[best.fit.table$a == m]
    
  } else if ("try-error" %in% class(fit_gamma) & "try-error" %in% class(fit_lnorm)){
    
    # if error with gamma and lnorm, try weibull first
    w <- gofstat(fit_weibull)
    
    # try fit llogis
    ll <- try(gofstat(fit_llogis), silent = TRUE)
    if ("try-error" %in% class(ll)){
      #only do weibull
      w <- gofstat(fit_weibull)
      # fit distribution to data
      a <- unlist(c(w[8]))
      best.fit.table <- data.table(c("weibull"), a)
      m <- min(a)
      b <- best.fit.table$V1[best.fit.table$a == m]
    }
    
    #Fit the best distribution to the data; identify it by the lowest anderson darling statistic
    a <- unlist(c(w[8], ll[8]))
    best.fit.table <- data.table(c("weibull", "llogis"), a)
    m <- min(a)
    b <- best.fit.table$V1[best.fit.table$a == m]
    
  } else if ("try-error" %in% class(fit_llogis) & "try-error" %in% class(fit_weibull)){
    
    # if error with llogis and weibull, try lnorm first
    ln <- gofstat(fit_lnorm)
    
    # try fit gamma
    g <- try(gofstat(fit_gamma), silent = TRUE)
    if ("try-error" %in% class(g)){
      #only do lnorm
      ln <- gofstat(fit_lnorm)
      # fit distribution to data
      a <- unlist(c(ln[8]))
      best.fit.table <- data.table(c("lnorm"), a)
      m <- min(a)
      b <- best.fit.table$V1[best.fit.table$a == m]
    }
    
    #Fit the best distribution to the data; identify it by the lowest anderson darling statistic
    a <- unlist(c(ln[8], g[8]))
    best.fit.table <- data.table(c("lnorm", "gamma"), a)
    m <- min(a)
    b <- best.fit.table$V1[best.fit.table$a == m]
    
  } else if ("try-error" %in% class(fit_gamma) & "try-error" %in% class(fit_lnorm)){
    # if error in gamma and lnorm, try the other two
    ll <- gofstat(fit_llogis)
    ln <- gofstat(fit_weibull)
    
    #Fit the best distribution to the data; identify it by the lowest anderson darling statistic
    a <- unlist(c(ll[8], ln[8]))
    best.fit.table <- data.table(c("llogis", "lnorm"), a)
    m <- min(a)
    b <- best.fit.table$V1[best.fit.table$a == m]
    
  } else if ("try-error" %in% class(fit_llogis)) {
    
    # if error in just llogis
    g <- gofstat(fit_gamma)
    ln <- gofstat(fit_lnorm)
    w <- gofstat(fit_weibull)
    
    #Fit the best distribution to the data; identify it by the lowest anderson darling statistic
    a <- unlist(c(g[8], ln[8], w[8]))
    best.fit.table <- data.table(c("gamma", "lnorm", "weibull"), a)
    m <- min(a)
    b <- best.fit.table$V1[best.fit.table$a == m]
    
  } else if ("try-error" %in% class(fit_gamma)) {
    
    # if error in just gamma
    ll <- gofstat(fit_llogis)
    ln <- gofstat(fit_lnorm)
    w <- gofstat(fit_weibull)
    
    #Fit the best distribution to the data; identify it by the lowest anderson darling statistic
    a <- unlist(c(ll[8], ln[8], w[8]))
    best.fit.table <- data.table(c("llogis", "lnorm", "weibull"), a)
    m <- min(a)
    b <- best.fit.table$V1[best.fit.table$a == m]
    
  } else if ("try-error" %in% class(fit_weibull)) {
    
    # if error in just weibull
    ll <- gofstat(fit_llogis)
    ln <- gofstat(fit_lnorm)
    g <- gofstat(fit_gamma)
    
    #Fit the best distribution to the data; identify it by the lowest anderson darling statistic
    a <- unlist(c(ll[8], ln[8], g[8]))
    best.fit.table <- data.table(c("llogis", "lnorm", "gamma"), a)
    m <- min(a)
    b <- best.fit.table$V1[best.fit.table$a == m]
    
  } else if ("try-error" %in% class(fit_lnorm)) {
    
    # if error in just lnorm
    ll <- gofstat(fit_llogis)
    g <- gofstat(fit_gamma)
    w <- gofstat(fit_weibull)
    
    #Fit the best distribution to the data; identify it by the lowest anderson darling statistic
    a <- unlist(c(ll[8], g[8], w[8]))
    best.fit.table <- data.table(c("llogis", "gamma", "weibull"), a)
    m <- min(a)
    b <- best.fit.table$V1[best.fit.table$a == m]
    
  } else {
    
    ll <- gofstat(fit_llogis)
    ln <- gofstat(fit_lnorm)
    g <- gofstat(fit_gamma)
    w <- gofstat(fit_weibull)
    
    #Fit the best distribution to the data; identify it by the lowest anderson darling statistic
    a <- unlist(c(ll[8], ln[8], g[8], w[8]))
    best.fit.table <- data.table(c("llogis", "lnorm", "gamma", "weibull"), a)
    m <- min(a)
    b <- best.fit.table$V1[best.fit.table$a == m]
    
  }

  
  #Calculate the best fit distribution
  best.fit <- fitdist(df$average, b)
  
  # Extract the estimated HC5 value
  hc5 <- quantile(best.fit, probs = 0.05)
  Estimated_HC5 <- hc5$quantiles$`p=0.05`
  
  # Bootstrap the HC5 value with upper and lower CIs
  fit_boot <- bootdist(best.fit, bootmethod = 'param', niter = 1000)
  
  # This step is not necessary I am just using it to check the bootstrap is working
  bootstrap_hc5 <- quantile(fit_boot, probs = 0.05)
  
  # Save boostrapped HC5 and CIs
  Bootstrapped_HC5 <- bootstrap_hc5$quantiles$`p=0.05`
  HC5_lower_ci <- bootstrap_hc5$quantCI[1,1]
  HC5_upper_ci <- bootstrap_hc5$quantCI[2,1]
  
  # Save the identifying variables
  Chem.ID <- unique(df$Chemical)
  Species.left.out <- unique(df$Sp.left.out)
  
  # Save the HC5 values
  hc5.table <- data.frame(i, k, Estimated_HC5, Bootstrapped_HC5, HC5_lower_ci, HC5_upper_ci, b, m, Species.left.out)
  
  # Save each line as a spot in the HC5 list
  individual.hc5s.for.chem[[k]] <- hc5.table
  
  }
  
  # Combine all the elements of the list together (don't overwrite)
  individual.hc5s.for.chem.1 <- rbindlist(individual.hc5s.for.chem)
  
  # Then save each all the runs for a single chemical together as a space in a list
  individual.hc5s[[i]] <- individual.hc5s.for.chem.1
  
}

# Finally, combine data from all chemicals together
individual.hc5s.LOO <- rbindlist(individual.hc5s)
```


### Check LOO loop output and clean up data
Quickly check the work we did to see it works
```{r}
# First check for duplicates (the loop may have ran through an extra time)
individual.hc5s.LOO <- unique(individual.hc5s.LOO)

# Change column names to match the other HC5 output
colnames(individual.hc5s.LOO) <- c("Chemical", "Iteration", "SSD Estimated HC5", "SSD Bootstrapped HC5", "HC5 Lower CI", "HC5 Upper CI", "SSD Dist.", "SSD AD", "Species Left Out")
```

We have calculated the single-chem HC5s, the single-chem LOO HC5s, and now we can move on to the SSDn HC5s.

# 4. Build normalized SSDs and extract the HC5n/HC5 values
Using this method, we will create the maximum number of SSDns possible, by first creating the maximum number of combinations of chemicals and by using all possible nSpecies within each combination.

### Initialize relevant variables before loop
```{r}
# Create a list of the organophosphate chemicals we are using
list.OPs <- c("Azinphos-methyl", "Chlorpyrifos", "Coumaphos", "Diazinon", "Dichlorvos", "Disulfoton", "EPN", "Fenitrothion", "Fenthion", "Malathion", "Methyl parathion", "Parathion", "Trichlorfon")

#Creates a list of different random draws from the 13 chemicals; each is for a different number of chemicals being drawn (m), and each draws the number of times (n) without repetition. Assigns the data.tables of these different chemical combinations to a variable called "chem.list.OP"
chem.list.OP <- list(
  data.table(comboSample(list.OPs, m = 2, n = 78, repetition = FALSE)), # 13 choose 2
  data.table(comboSample(list.OPs, m = 3, n = 286, repetition = FALSE)), # 13 choose 3
  data.table(comboSample(list.OPs, m = 4, n = 715, repetition = FALSE)), # 13 choose 4
  data.table(comboSample(list.OPs, m = 5, n = 1287, repetition = FALSE)), # 13 choose 5
  data.table(comboSample(list.OPs, m = 6, n = 1716, repetition = FALSE)), # 13 choose 6 
  data.table(comboSample(list.OPs, m = 7, n = 1716, repetition = FALSE)), # 13 choose 7 
  data.table(comboSample(list.OPs, m = 8, n = 1287, repetition = FALSE)), # 13 choose 8 
  data.table(comboSample(list.OPs, m = 9, n = 715, repetition = FALSE)), # 13 choose 9 
  data.table(comboSample(list.OPs, m = 10, n = 286, repetition = FALSE)), # 13 choose 10 
  data.table(comboSample(list.OPs, m = 11, n = 78, repetition = FALSE)), # 13 choose 11
  data.table(comboSample(list.OPs, m = 12, n = 13, repetition = FALSE)), # 13 choose 12
  data.table(comboSample(list.OPs, m = 13, n = 1, repetition = FALSE))) # 13 choose 13

#check
chem.list.OP[[1]]
```

### Initialize the loop - using chem.list.OP
```{r}
# Initialize the data vectors - these are empty lists that will store the outputs of the loop so we can combine them later
statvec <- c()
numbers <- c()
Compounds <- list()
List.Statsdf <- list()
List.Compounds <- list()

# This loop iterates through the groupings of chemicals: in this case, we have our list of organophosphates with 12 different groupings (2 chems, 3 chems, 4 chems, 5 chems...13 chems).
for (y in 1:12) {
  
  current.chem.list <- chem.list.OP[[y]] # index the current chemicals
  Statsdf <- list() # make a list to hold the outputs
  xlength <- length(current.chem.list$V1) # finds how many different groups there are within that group (ie there are 10 pairs of 2 chems)

# This next loop is nested within the first loop. It takes the chemicals within the group we are looking at, makes a data frame matching those chemicals
for (x in 1:xlength) {
  
  OP.chemicals <- current.chem.list[x]
  
#Making a dataframe using only chemicals with the same MOA, for a single water type
OP.data <- data %>%
  filter(Chemical %in% OP.chemicals)

#Select species from each compound of interest
ListByChemical <- list()

# This loop iterates through each chemical in our list.
for (Chemical_ in OP.chemicals){
  
  # Set the current chemical to the chemical of interest
  CurrentCompound <- Chemical_
  
  # Filter the species to include only species from the current compound of all the species in the data set
  CurrentCompoundSpecies <- OP.data %>%
    filter(Chemical == CurrentCompound & Species %in% data$Species)
  
  #Makes a list of species but each species is only represented one time
  SingleList<- unique(CurrentCompoundSpecies$Species)
  
  #This assigns the newly made vector of species for a chemical to the next item of the list. The double bracket [[i]] is the index number of where it is located in that list.
  ListByChemical[[Chemical_]] <- SingleList
  
}

# Create a vector of species that are shared across all chemicals (ie our nSpecies pool)
xspecies <- Reduce(intersect, ListByChemical)

# The next loop iterates through this nSpecies pool and sets each as the normalization species, so it can be used to calculate the LC50n values

# initialize list for holding data
byspecies.df <- list()

for(xspecies_ in xspecies){

  # Set the normalization species
  commonspecies <- xspecies_ 
  
  # Create a data frame of toxicity data for just the normalization species (eg only daphnia magna, for example)
  ToxSensitive <- OP.data %>%
    filter(Species == commonspecies)

  # Calculate the geometric mean of the nSpecies toxicity (also called the SMAV of the nSpecies)
  ToxSensitive <- ToxSensitive %>%
    group_by(Chemical) %>% # group by each chemical
    summarise(
    average = geoMean(Conc)) #SMAV of the nSpecies

# We now have the nSpecies SMAVs calculated for each chemical. The next loop will calculate LC50n values for one chemical group at a time. It will assign them to a list of data frames. To calculate LC50n values you divide the LC50 by the nSpecies SMAV
# LC50n values are calculated by dividing the LC50 by the normalizing species 

# Set up empty lists for holding data
df.bf <- list()
chem.no.spec <- list()

# This loop iterates through each chemical - for each chemical in the list of organophosphate:
for(Chemical_ in OP.chemicals){
  
  # Filter the data for only that chemical
  ICE1 <- OP.data %>%
    filter(Chemical == Chemical_)
  
  # Save the nSpecies SMAV for that chemical as the average value
  avgval <- ToxSensitive$average[ToxSensitive$Chemical == Chemical_]
  
  # Calculate the SMAV for each species for a SINGLE chemical
  ICE2 <- ICE1 %>%
    group_by(Species) %>% # group by species to account for multiple observations
    summarise(
      SMAV = geoMean(Conc), # Calculate the SMAV for each species for a single chemical
      Genus = Genus
    ) %>%
    mutate(SMAV.norm = SMAV/avgval) # Normalize SMAVs for each species for a single chemical using the average value of the nSpecies
  
  # Remove duplicate values
  ICE2 <- unique(ICE2)
  
  # Save the results into the individual chemical's list
  df.bf[[Chemical_]] <- ICE2
  
  # Order the species for this chemical by the SMAV
  df.nSpecies <- ICE2[order(ICE2$SMAV.norm),]
  
  # Find the cumulative probability of each species SMAV (as you would in a regular SSD)
  df.nSpecies$P <- ppoints(df.nSpecies$SMAV.norm, 0.5)
  
  # Find the cumulative probability of the nSpecies for that chemical
  nSpecies.P.chem <- df.nSpecies$P[df.nSpecies$Species == commonspecies]
  
  # Save that into a data frame
  data.frame(nSpecies.P.chem)
  
  # Save all of this data into the list
  chem.no.spec[[Chemical_]] <- data.table(Chemical_, length(ICE2$SMAV.norm), length(unique(ICE2$Genus)), nSpecies.P.chem)
  
}

# These tables combine all the separate tables with LC50n values
Newdf.bf <- rbindlist(df.bf)
chem.no.spec <- rbindlist(chem.no.spec)
colnames(chem.no.spec) <- c("Chemical", "no.species", "no.genera", "nSpecies.P.chem")
chem.no.spec <- chem.no.spec %>%
  mutate(nSpecies.P.chem.SEM = std.error(nSpecies.P.chem))
tot.data <- length(Newdf.bf$Species)


# We now have all the LC50n values for all species and all chemicals


# This next section of the loop creates the SSDn using the LC50n values for all of the compounds

# Derive the geometric mean of normalized SMAVs across all chemicals
Newdf.bf <- Newdf.bf %>%
  group_by(Species) %>%
  summarise(
    SMAV.norm = geoMean(SMAV.norm), # geometric mean of normalized SMAV
    Genus = Genus,
    n = n())

# Remove any duplicates
Newdf.bf <- unique(Newdf.bf)

# Order by normalized SMAV and find cumulative probability
df <- Newdf.bf[order(Newdf.bf$SMAV.norm),]
df$frac <- ppoints(Newdf.bf$SMAV.norm, 0.5)

# Make it a data table
df <- data.table(df)

#Fit a distribution to the plotted points - there might be errors here so have built in de-bugging
fit_llogis <- try(fitdist(df$SMAV.norm, "llogis"), silent = TRUE) # there might be an error, see if there is
fit_lnorm <- try(fitdist(df$SMAV.norm, "lnorm"), silent = TRUE) # there might be an error, see if there is
fit_gamma <- try(fitdist(df$SMAV.norm, "gamma"), silent = TRUE) # there might be an error, see if there is
fit_weibull <- try(fitdist(df$SMAV.norm, "weibull"), silent = TRUE) # there might be an error, see if there is

  # If there is an error in all 4 cases, return that there is an error.
if("try-error" %in% class(fit_gamma) & "try-error" %in% class(fit_llogis) & "try-error" %in% class(fit_weibull) & "try-error" %in% class(fit_lnorm)){
    
    # Paste that there is an error with all 4
    paste("there is an error with all 4 distributions")

  } else if ("try-error" %in% class(fit_gamma) & "try-error" %in% class(fit_llogis) & "try-error" %in% class(fit_weibull)){
    
    # If there is error with gamma, llogis, and weibull, only do lognormal
    ln <- gofstat(fit_lnorm)
    #Fit the best distribution to the data; identify it by the lowest anderson darling statistic
    a <- unlist(c(ln[8]))
    best.fit.table <- data.table(c("lnorm"), a)
    m <- min(a)
    b <- best.fit.table$V1[best.fit.table$a == m]
    
  } else if ("try-error" %in% class(fit_gamma) & "try-error" %in% class(fit_llogis) & "try-error" %in% class(fit_lnorm)){
    
    # If there is error with gamma, llogis, and lnorm, only do weibull
    w <- gofstat(fit_weibull)
    #Fit the best distribution to the data; identify it by the lowest anderson darling statistic
    a <- unlist(c(w[8]))
    best.fit.table <- data.table(c("weibull"), a)
    m <- min(a)
    b <- best.fit.table$V1[best.fit.table$a == m]
    
  } else if ("try-error" %in% class(fit_gamma) & "try-error" %in% class(fit_weibull) & "try-error" %in% class(fit_lnorm)){
    
    # If there is error with gamma, weibull, and lnorm, only do llogis
    ll <- gofstat(fit_llogis)
    #Fit the best distribution to the data; identify it by the lowest anderson darling statistic
    a <- unlist(c(ll[8]))
    best.fit.table <- data.table(c("llogis"), a)
    m <- min(a)
    b <- best.fit.table$V1[best.fit.table$a == m]
    
  } else if ("try-error" %in% class(fit_llogis) & "try-error" %in% class(fit_weibull) & "try-error" %in% class(fit_lnorm)){
    
    # If there is error with llogis, weibull, and lnorm, only do gamma
    g <- gofstat(fit_gamma)
    #Fit the best distribution to the data; identify it by the lowest anderson darling statistic
    a <- unlist(c(g[8]))
    best.fit.table <- data.table(c("gamma"), a)
    m <- min(a)
    b <- best.fit.table$V1[best.fit.table$a == m]
    
  } else if ("try-error" %in% class(fit_gamma) & "try-error" %in% class(fit_llogis)){
    
    # if error with gamma and llogis, try lnorm first
    ln <- gofstat(fit_lnorm)
    
    # try to also fit weibull
    w <- try(gofstat(fit_weibull), silent = TRUE)
    if ("try-error" %in% class(w)){
      
      #only do lnorm
      ln <- gofstat(fit_lnorm)
      # fit distribution to data
      a <- unlist(c(ln[8]))
      best.fit.table <- data.table(c("lnorm"), a)
      m <- min(a)
      b <- best.fit.table$V1[best.fit.table$a == m]
    }
    
    #Fit the best distribution to the data; identify it by the lowest anderson darling statistic
    a <- unlist(c(ln[8], w[8]))
    best.fit.table <- data.table(c("lnorm", "weibull"), a)
    m <- min(a)
    b <- best.fit.table$V1[best.fit.table$a == m]
    
  } else if ("try-error" %in% class(fit_gamma) & "try-error" %in% class(fit_weibull)){
    
    # if error with gamma and weibull, try lnorm first
    ln <- gofstat(fit_lnorm)
    
    # try to also fit llogis
    ll <- try(gofstat(fit_llogis), silent = TRUE)
    if ("try-error" %in% class(ll)){
      #only do lnorm
      ln <- gofstat(fit_lnorm)
      # fit distribution to data
      a <- unlist(c(ln[8]))
      best.fit.table <- data.table(c("lnorm"), a)
      m <- min(a)
      b <- best.fit.table$V1[best.fit.table$a == m]
    }
    
    #Fit the best distribution to the data; identify it by the lowest anderson darling statistic
    a <- unlist(c(ln[8], ll[8]))
    best.fit.table <- data.table(c("lnorm", "llogis"), a)
    m <- min(a)
    b <- best.fit.table$V1[best.fit.table$a == m]
    
  } else if ("try-error" %in% class(fit_gamma) & "try-error" %in% class(fit_lnorm)){
    
    # if error with gamma and lnorm, try weibull first
    w <- gofstat(fit_weibull)
    
    # try fit llogis
    ll <- try(gofstat(fit_llogis), silent = TRUE)
    if ("try-error" %in% class(ll)){
      #only do weibull
      w <- gofstat(fit_weibull)
      # fit distribution to data
      a <- unlist(c(w[8]))
      best.fit.table <- data.table(c("weibull"), a)
      m <- min(a)
      b <- best.fit.table$V1[best.fit.table$a == m]
    }
    
    #Fit the best distribution to the data; identify it by the lowest anderson darling statistic
    a <- unlist(c(w[8], ll[8]))
    best.fit.table <- data.table(c("weibull", "llogis"), a)
    m <- min(a)
    b <- best.fit.table$V1[best.fit.table$a == m]
    
  } else if ("try-error" %in% class(fit_llogis) & "try-error" %in% class(fit_weibull)){
    
    # if error with llogis and weibull, try lnorm first
    ln <- gofstat(fit_lnorm)
    
    # try fit gamma
    g <- try(gofstat(fit_gamma), silent = TRUE)
    if ("try-error" %in% class(g)){
      #only do lnorm
      ln <- gofstat(fit_lnorm)
      # fit distribution to data
      a <- unlist(c(ln[8]))
      best.fit.table <- data.table(c("lnorm"), a)
      m <- min(a)
      b <- best.fit.table$V1[best.fit.table$a == m]
    }
    
    #Fit the best distribution to the data; identify it by the lowest anderson darling statistic
    a <- unlist(c(ln[8], g[8]))
    best.fit.table <- data.table(c("lnorm", "gamma"), a)
    m <- min(a)
    b <- best.fit.table$V1[best.fit.table$a == m]
    
  } else if ("try-error" %in% class(fit_gamma) & "try-error" %in% class(fit_lnorm)){
    # if error in gamma and lnorm, try the other two
    ll <- gofstat(fit_llogis)
    ln <- gofstat(fit_weibull)
    
    #Fit the best distribution to the data; identify it by the lowest anderson darling statistic
    a <- unlist(c(ll[8], ln[8]))
    best.fit.table <- data.table(c("llogis", "lnorm"), a)
    m <- min(a)
    b <- best.fit.table$V1[best.fit.table$a == m]
    
  } else if ("try-error" %in% class(fit_llogis)) {
    
    # if error in just llogis
    g <- gofstat(fit_gamma)
    ln <- gofstat(fit_lnorm)
    w <- gofstat(fit_weibull)
    
    #Fit the best distribution to the data; identify it by the lowest anderson darling statistic
    a <- unlist(c(g[8], ln[8], w[8]))
    best.fit.table <- data.table(c("gamma", "lnorm", "weibull"), a)
    m <- min(a)
    b <- best.fit.table$V1[best.fit.table$a == m]
    
  } else if ("try-error" %in% class(fit_gamma)) {
    
    # if error in just gamma
    ll <- gofstat(fit_llogis)
    ln <- gofstat(fit_lnorm)
    w <- gofstat(fit_weibull)
    
    #Fit the best distribution to the data; identify it by the lowest anderson darling statistic
    a <- unlist(c(ll[8], ln[8], w[8]))
    best.fit.table <- data.table(c("llogis", "lnorm", "weibull"), a)
    m <- min(a)
    b <- best.fit.table$V1[best.fit.table$a == m]
    
  } else if ("try-error" %in% class(fit_weibull)) {
    
    # if error in just weibull
    ll <- gofstat(fit_llogis)
    ln <- gofstat(fit_lnorm)
    g <- gofstat(fit_gamma)
    
    #Fit the best distribution to the data; identify it by the lowest anderson darling statistic
    a <- unlist(c(ll[8], ln[8], g[8]))
    best.fit.table <- data.table(c("llogis", "lnorm", "gamma"), a)
    m <- min(a)
    b <- best.fit.table$V1[best.fit.table$a == m]
    
  } else if ("try-error" %in% class(fit_lnorm)) {
    
    # if error in just lnorm
    ll <- gofstat(fit_llogis)
    g <- gofstat(fit_gamma)
    w <- gofstat(fit_weibull)
    
    #Fit the best distribution to the data; identify it by the lowest anderson darling statistic
    a <- unlist(c(ll[8], g[8], w[8]))
    best.fit.table <- data.table(c("llogis", "gamma", "weibull"), a)
    m <- min(a)
    b <- best.fit.table$V1[best.fit.table$a == m]
    
  } else {
    
    ll <- gofstat(fit_llogis)
    ln <- gofstat(fit_lnorm)
    g <- gofstat(fit_gamma)
    w <- gofstat(fit_weibull)
    
    #Fit the best distribution to the data; identify it by the lowest anderson darling statistic
    a <- unlist(c(ll[8], ln[8], g[8], w[8]))
    best.fit.table <- data.table(c("llogis", "lnorm", "gamma", "weibull"), a)
    m <- min(a)
    b <- best.fit.table$V1[best.fit.table$a == m]
    
  }

# Calculate the best fit distribution
best.fit <- fitdist(df$SMAV.norm, b)

# Save the distribution parameters
params <- names(best.fit[[1]])
params.no <- best.fit[[1]]
param1 <- params[1]
param2 <- params[2]
param1.no <- params.no[1]
param2.no <- params.no[2]

# List of the distribution parameters SDs
params.sd <- best.fit[[3]]
param1.sd <- params.sd[1]
param2.sd <- params.sd[2]

# Calculate a normalized hc5 value with a bootstrap
hc5n <- quantile(best.fit, probs = 0.05)
hc5n <- hc5n$quantiles$`p=0.05`

# Combine all the data from a single run together
data.table(ToxSensitive)
data.table(chem.no.spec)

# Create a joint data frame with the following variables
jointdf <- full_join(ToxSensitive, chem.no.spec, by = "Chemical")
jointdf$iteration <- x # save which iteration it was calculated on
jointdf$bf.HC5n <- hc5n # the hc5n of the SSDn
jointdf$bf.HC5 <- jointdf$average * hc5n #the chemical specific HC5 using the best fit distribution 
jointdf$no.chems <- length(ToxSensitive$Chemical) # number of chemicals used to make the SSDn
jointdf$dist <- b #type of distribution
jointdf$param1 <- param1 # model parameters
jointdf$param1.no <- param1.no # model parameters
jointdf$param1.sd <- param1.sd # model parameters
jointdf$param2 <- param2 # model parameters
jointdf$param2.no <- param2.no # model parameters
jointdf$param2.sd <- param2.sd # model parameters
jointdf$tot.data <- tot.data # total number of SMAVs contributed to the SSDn
jointdf$AIC <- m # Anderson darling stat for the SSDn best fit distribution
jointdf$nSpecies.P.SSDn <- df$frac[df$Species == commonspecies] # cumulative probability of the nSpecies in the SSDn
jointdf$nSpecies <- commonspecies # which nSpecies used in this iteration
jointdf$tot.species <- length(df$Species)# How many species in the SSDn
jointdf$tot.genera <- length(unique(df$Genus)) #How many genera in the SSDn

# index this data to which species made the SSDn
byspecies.df[[xspecies_]] <- jointdf

}

Statsdf[[x]] <- rbindlist(byspecies.df)
Statsdf


}
  List.Statsdf[[y]] <- rbindlist(Statsdf) #Add to the overall output dataframe list for each run with diff. no. of chems
}

# Save this before we over write it
List.Statsdf.combo <- rbindlist(List.Statsdf)
```


The "List.Statsdf.combo" is the raw output of all the SSDns we created using the loop. Before moving on to further analyses, it will be helpful to calculate relevant statistics and variables.

### Calculate means, SDs, SEs, and 95% CIs for the nSpecies and overall
There should be the HC5 for each species, and the overall chemical HC5 which is calculated by averaging all of the HC5s for the species for a single chemical. 

We are interested in the overall chemical mean rather than the nSpecies means as some species have a lot more data than others; if we only used each value to calculate the overall mean, we would weight the results to the species with more data - which we do not want to do.
```{r}
# First, calculate the means, standard deviations, standard errors, and 95% confidence intervals around the nSpecies mean and overall chemical mean
Final.Data <- List.Statsdf.combo %>%
  dplyr::group_by(Chemical, nSpecies) %>% # first group by chemical then group by the nSpecies
  mutate(
    nspecies.mean.HC5 = mean(bf.HC5)) %>% # Calculate the mean HC5 for that nSpecies
  dplyr::ungroup() %>% # ungroup
  dplyr::group_by(Chemical) %>% # group by chemical
  mutate(
    chemical.mean.HC5 = mean(nspecies.mean.HC5), # calculate the overall average HC5 for that chemical (take the mean of a mean)
    chemical.sd.HC5 = sd(nspecies.mean.HC5), # calculate overall SD for each chemical
    no.obs.length = length(unique(nSpecies)), # calculate how many nSpecies were used for each chemical
    chemical.std.err.HC5 = (chemical.sd.HC5 / sqrt(no.obs.length)), # calculate standard error by dividing the SD by the square root of the sample size - in this case, how many nspecies there are 
    upper.CI = (chemical.mean.HC5 + 1.96*chemical.std.err.HC5), # calculate upper 95% CI
    lower.CI = (chemical.mean.HC5 - 1.96*chemical.std.err.HC5), # calculate lower 95% CI
    upper.SD.limit = (chemical.mean.HC5 + chemical.sd.HC5), # calculate mean + 1 SD
    lower.SD.limit = (chemical.mean.HC5 - chemical.sd.HC5)) %>% # mean - 1 SD
  dplyr::ungroup() # ungroup chemical so data is back how it was
```

### Add the single chemical HC5s to the final dataset
Add the single chemical HC5s (true HC5s) to the data - this is helpful for a few of the plots
```{r}
# Extract the chemical specific HC5s
single.hc5.table <- single.individual.HC5s %>%
  dplyr::select(Chemical, `SSD Estimated HC5`)
  
# Rename the columns so I can join to the full dataset
colnames(single.hc5.table) <- c("Chemical", "Single.C.HC5.bf")

# Join to full data set
Final.Data <- left_join(Final.Data, single.hc5.table, by = "Chemical")
```

We have added all relevant data and variables to our final dataset, which we can now use to make plots. 

# 5. Summarize and prepare plotting data

### Prepare LOO vs SSDn comparison data
The steps in this code chunk are pretty bulky, but what I am trying to do here with the wide vs long data is two things. First, by making the data into wide data I can export it cleanly as a table, which can go straight into the manuscript. The long data is needed specifically for plotting.
```{r}
### Generate the LOO plotting data
LOO.plotting.data.wide <- individual.hc5s.LOO %>%
  dplyr::select(Chemical, Iteration, `SSD Estimated HC5`) %>% # select only these columns
  dplyr::group_by(Chemical) %>% # group by chemical
  mutate(
    LOO.mean.HC5 = mean(`SSD Estimated HC5`), # calculate mean
    LOO.SD.HC5 = sd(`SSD Estimated HC5`), # calculate SD
    LOO.std.err = LOO.SD.HC5 / sqrt(length(Iteration)), # calculate standard error
    LOO.upper.CI = (LOO.mean.HC5 + 1.96*LOO.std.err), # calculate upper CI
    LOO.lower.CI = (LOO.mean.HC5 - 1.96*LOO.std.err), # calculate lower CI
    LOO.SD.upper = (LOO.mean.HC5 + LOO.SD.HC5), # calculate mean + SD
    LOO.SD.lower = (LOO.mean.HC5 - LOO.SD.HC5)) %>% # calculate mean - SD
  ungroup() # ungroup to revert data back to how it was

# Select only the mean/sd/se/ci columns
LOO.plotting.data.wide <- LOO.plotting.data.wide[ ,c(1,4:10)]
# Remove duplicates
LOO.plotting.data.wide <- unique(LOO.plotting.data.wide)

# Now we have a nice summary table of the HC5 data using the LOO method

### Clean the SSDn plotting data
SSDn.plotting.data.wide <- Final.Data %>%
  dplyr::select(
    Chemical, chemical.mean.HC5, chemical.sd.HC5, chemical.std.err.HC5, upper.CI, lower.CI, upper.SD.limit, lower.SD.limit) %>%
  unique()

# Same with the SSDn method

# Combine the two together so we can convert to long format
combined.plot.data <- left_join(LOO.plotting.data.wide, SSDn.plotting.data.wide)

# First extract just the means and convert to long format
long.data.means <- combined.plot.data %>%
  dplyr::select(Chemical, LOO.mean.HC5, chemical.mean.HC5) %>% # select only the chemical and two mean variables
  pivot_longer(cols = c("LOO.mean.HC5", "chemical.mean.HC5"), # pivot longer 
               names_to = "Method",
               values_to = "HC5.Mean.Estimate")
# Rename the method to LOO vs SSDn
long.data.means[long.data.means == "LOO.mean.HC5"] <- "LOO"
long.data.means[long.data.means == "chemical.mean.HC5"] <- "SSDn"

# Now do same for SDs
long.data.SDs <- combined.plot.data %>%
  dplyr::select(Chemical, LOO.SD.HC5, chemical.sd.HC5)%>%
  pivot_longer(cols = c("LOO.SD.HC5", "chemical.sd.HC5"),
               names_to = "Method",
               values_to = "HC5.SD.Estimate")
# Rename the method to LOO vs SSDn
long.data.SDs[long.data.SDs == "LOO.SD.HC5"] <- "LOO"
long.data.SDs[long.data.SDs == "chemical.sd.HC5"] <- "SSDn"

# Now do same for standard errors
long.data.SEs <- combined.plot.data %>%
  dplyr::select(Chemical, LOO.std.err, chemical.std.err.HC5)%>%
  pivot_longer(cols = c("LOO.std.err", "chemical.std.err.HC5"),
               names_to = "Method",
               values_to = "HC5.Std.Err.Estimate")
# Rename the method to LOO vs SSDn
long.data.SEs[long.data.SEs == "LOO.std.err"] <- "LOO"
long.data.SEs[long.data.SEs == "chemical.std.err.HC5"] <- "SSDn"

# Combine together
long.data.total <- left_join(long.data.means, long.data.SDs)
long.data.total <- left_join(long.data.total, long.data.SEs)

# add in upper and lower CIs
long.data.total <- long.data.total %>%
  dplyr::mutate(
    HC5.Upper.CI = HC5.Mean.Estimate + 1.96*HC5.Std.Err.Estimate,
    HC5.Lower.CI = HC5.Mean.Estimate - 1.96*HC5.Std.Err.Estimate)
```



## Add in single chem SSD upper and lower CI to long data total
We want to compare the CIs for all three methods. For the conventional SSD method, we are using the upper and lower confidence interval of the best-fit distribution.
```{r}
###
single.individual.HC5s
single.ssd.long <- single.individual.HC5s %>%
  dplyr::select(Chemical, `SSD Estimated HC5`, `HC5 Lower CI`, `HC5 Upper CI`)

## add in relevant columns
single.ssd.long$Method <- "SSD"
single.ssd.long$HC5.SD.Estimate <- NA
single.ssd.long$HC5.Std.Err.Estimate <- NA

# re order the columns
single.ssd.long <- single.ssd.long[, c(1,5,2,6,7,4,3)] # leave the row index blank to keep all rows

# rename columns
colnames(single.ssd.long)[3] <- "HC5.Mean.Estimate"
colnames(single.ssd.long)[6] <- "HC5.Upper.CI"
colnames(single.ssd.long)[7] <- "HC5.Lower.CI"

long.data.total <- rbind(long.data.total, single.ssd.long)
```

# 6. Calculate some accuracy and uncertainty metrics

I am going to calculate fold-difference as the primary measure of accuracy (as in fold increase or decrease) and a ratio of the upper confidence interval to the estimate as a measure of uncertainty.

### Create a function for calculating the absolute value of fold-difference
```{r}
# Create the function. The fold difference gives the absolute value of the maximum of the two numbers being compared. If you want to look for directionality to determine if one value is lower than the other, then also compute the actual difference as chemA/chemB and just remember which one is your numerator and which is your denominator. I always calculate an actual difference every time I work with fold difference to ensure there isnt a bias in over or under-estimation.
fold.diff <- function(prediction, actual) {
  return(max(prediction/actual, actual/prediction))
}

## test
fold.diff(10, 20)
fold.diff(20, 10)

# So what is happening here is we are simply getting the absolute value of the fold difference, which makes sense for our plots. IE going from 20 to 10 is a 2-fold decrease, and going from 10 to 20 is a 2-fold increase. Similarly, going from 5 to 10 is also a 2-fold increase, and 10 to 5 is a 2-fold decrease.
```


### Add in the single-chemical SSD HC5s to the long-data total dataset
```{r}
# Select the chemical and the single chemical HC5 columns and save as new dataframe
SSD.HC5s <- single.individual.HC5s %>%
  dplyr::select(Chemical, `SSD Estimated HC5`)

# Join them to the metric data frame
metric.data <- left_join(long.data.total, SSD.HC5s)

# Rename column names
colnames(metric.data)[8] <- "Single.SSD.HC5"
```




### Calculate an accuracy metric based on the fold-difference
```{r}
# the function does not work for data frames, so we have to apply it using a loop

### Set up a n empty list to hold the accuracy results along with the chemical identifier
accuracy.list <- list()
for (i in 1:nrow(metric.data)){
  Chemical <- metric.data$Chemical[i]
  Method <- metric.data$Method[i]
  Accuracy <- fold.diff(metric.data$HC5.Mean.Estimate[i], metric.data$Single.SSD.HC5[i])
  accuracy.list[[i]] <- data.table(Chemical, Method, Accuracy)
}

# Make it into a data frame
accuracy.list <- rbindlist(accuracy.list)

# Join into the accuracy test data frame
metric.data <- left_join(metric.data, accuracy.list)
```




### Uncertainty metric
The uncertainty metric we developed is the ratio of the SSDn upper CI to the SSDn HC5 average, given as A/B where A is the SSDn upper CI and B is the SSDn HC5 average.
In this metric, the closer you get to 1, the more certain you are. And the further away you get from 1, the more uncertain you are.
```{r}
### Create a test data frame with the metric
metric.data <- metric.data %>% # take from metric data
  dplyr::mutate(
    Uncertainty = HC5.Upper.CI/HC5.Mean.Estimate) # create the metric

# We have the metric, now we need to add in relevant factors that we think might be affecting uncertainty (so we can run a linear model/regression)

### Add in number of species in original single chemical SSD

# Filter and summarize the data to see which chemicals have the most species
no.spec.in.SSD.data <- data %>% 
  dplyr::group_by(Chemical) %>% # group by chemical
  summarise(
    number_species = n_distinct(Species)) %>% # calculate number of species
  arrange(desc(number_species)) # arrange in descending order (most species at top)

### join to uncertainty test data
metric.data <- left_join(metric.data, no.spec.in.SSD.data)

### Rename column name
colnames(metric.data)[11] <- "Number.Species.in.SSD"


# Now add in the number of nSpecies (take this from the final data)
### add in number of nSpecies
no.n.spec <- Final.Data %>%
  dplyr::group_by(Chemical) %>%
  summarise(
    no.n.species = n_distinct(nSpecies)) %>% # calculate number of species
  arrange(desc(no.n.species)) # arrange in descending order (most species at top)

### Left join this into the uncertainty data
metric.data <- left_join(metric.data, no.n.spec)

### Rename column name
colnames(metric.data)[12] <- "Number.nSpecies.in.SSDn"
```


### Add in the range of min-max tox values from single-chemical SSD
```{r}
# Range in min-max tox values from single-chemical SSD
ssd.range <- data %>%
  dplyr::group_by(Chemical) %>%
  summarise(
    Chemical = Chemical,
    min.SSD.tox.val = min(Conc), # take min tox value
    max.SSD.tox.val = max(Conc), # take max tox value 
    min.max.SSD.range = max.SSD.tox.val - min.SSD.tox.val # take difference between them
  )

# Take only unique values
ssd.range <- unique(ssd.range)

# Join to metric data set
metric.data <- left_join(metric.data, ssd.range)
```



### Export the metric data as a CVS file so it can be used to create a table
```{r}
write.csv(metric.data, "OP_Fish_metric_data.csv")
```

#7. Create plots and figures

### Update the factor levels
I need to split this into two different plots.
```{r}
# Make the Method a factor

# Make test data frame
plot.1.data <- long.data.total
  
plot.1.data <- plot.1.data %>%
  filter(
    Chemical == "Azinphos-methyl" | Chemical == "Chlorpyrifos" | Chemical ==  "Malathion" | Chemical == "EPN" | Chemical ==  "Disulfoton" | Chemical ==  "Dichlorvos"
  )

# make method a factor with these levels to match the plot
plot.1.data$Method <- factor(plot.1.data$Method, levels = c("SSD", "LOO", "SSDn"))

# manually change the factor levels of the chemicals so that it goes in order from smallest HC5 to largest HC5
plot.1.data$Chemical <- factor(plot.1.data$Chemical, levels = c("Azinphos-methyl", "Chlorpyrifos", "Malathion","EPN", "Disulfoton", "Dichlorvos"))

```


### Comparison plot including the single-chemical HC5 as well
This plot has three values, the LOO HC5 mean and CI, the single-chemical HC5, and the SSDn HC5 mean and CI.
```{r}
# first make long data a factor so it can be plotted
plot.1.data$Method <- as.factor(plot.1.data$Method)


# set up color palette
comp.plot.colours <- c(SSD = "#000000", LOO = "#000000", SSDn = "#000000") # color palette (all black)
comp.plot.shapes <- c(SSD = 17, LOO = 19, SSDn = 15) # shape types


# Create a comparison plot
comp.plot.1 <- plot.1.data %>%
  ggplot()+
  aes(x = Chemical, y = HC5.Mean.Estimate, ymin = HC5.Lower.CI, ymax = HC5.Upper.CI, color = Method, shape = Method)+
  geom_point(size = 2.5, position = position_dodge(width = 1))+ # add in the points, dodge so they don't hit or overlap each other
  geom_linerange(aes(ymax= HC5.Upper.CI, ymin = pmax(HC5.Lower.CI, 0)), size = 1, position = position_dodge(width = 1))+ # set line ranges as the upper and lower CIs
  geom_vline(xintercept = 1.5)+ # add in vertical line to separate chemicals
  geom_vline(xintercept = 2.5)+ # add in vertical line to separate chemicals
  geom_vline(xintercept = 3.5)+ # add in vertical line to separate chemicals
  geom_vline(xintercept = 4.5)+ # add in vertical line to separate chemicals
  geom_vline(xintercept = 5.5)+ # add in vertical line to separate chemicals
  geom_segment(aes(x = 0.5, xend = 1.5, 
                   y = unique(Final.Data$Single.C.HC5.bf[Final.Data$Chemical == "Azinphos-methyl"]*5), 
                   yend = unique(Final.Data$Single.C.HC5.bf[Final.Data$Chemical == "Azinphos-methyl"]*5)),
               colour = "black", linetype = "dashed")+ # add in 5 fold upper for Azinphos-methyl
  geom_segment(aes(x = 0.5, xend = 1.5, 
                   y = unique(Final.Data$Single.C.HC5.bf[Final.Data$Chemical == "Azinphos-methyl"]/5), 
                   yend = unique(Final.Data$Single.C.HC5.bf[Final.Data$Chemical == "Azinphos-methyl"]/5)),
               colour = "black", linetype = "dashed")+ # add in 5 fold lower for Azinphos-methyl
  geom_segment(aes(x = 0.5, xend = 1.5, 
                   y = unique(Final.Data$Single.C.HC5.bf[Final.Data$Chemical == "Azinphos-methyl"]*3), 
                   yend = unique(Final.Data$Single.C.HC5.bf[Final.Data$Chemical == "Azinphos-methyl"]*3)),
               colour = "black", linetype = "dotted")+ # add in 3 fold upper for Azinphos-methyl
  geom_segment(aes(x = 0.5, xend = 1.5, 
                   y = unique(Final.Data$Single.C.HC5.bf[Final.Data$Chemical == "Azinphos-methyl"]/3), 
                   yend = unique(Final.Data$Single.C.HC5.bf[Final.Data$Chemical == "Azinphos-methyl"]/3)),
               colour = "black", linetype = "dotted")+ # add in 3 fold lower for Azinphos-methyl
  geom_segment(aes(x = 1.5, xend = 2.5, 
                   y = unique(Final.Data$Single.C.HC5.bf[Final.Data$Chemical == "Chlorpyrifos"]*5), 
                   yend = unique(Final.Data$Single.C.HC5.bf[Final.Data$Chemical == "Chlorpyrifos"]*5)),
               colour = "black", linetype = "dashed")+ # add in 5 fold upper for Chlorpyrifos
  geom_segment(aes(x = 1.5, xend = 2.5, 
                   y = unique(Final.Data$Single.C.HC5.bf[Final.Data$Chemical == "Chlorpyrifos"]/5), 
                   yend = unique(Final.Data$Single.C.HC5.bf[Final.Data$Chemical == "Chlorpyrifos"]/5)),
               colour = "black", linetype = "dashed")+ # add in 5 fold lower for Chlorpyrifos
  geom_segment(aes(x = 1.5, xend = 2.5, 
                   y = unique(Final.Data$Single.C.HC5.bf[Final.Data$Chemical == "Chlorpyrifos"]*3), 
                   yend = unique(Final.Data$Single.C.HC5.bf[Final.Data$Chemical == "Chlorpyrifos"]*3)),
               colour = "black", linetype = "dotted")+ # add in 3 fold upper for Chlorpyrifos
  geom_segment(aes(x = 1.5, xend = 2.5, 
                   y = unique(Final.Data$Single.C.HC5.bf[Final.Data$Chemical == "Chlorpyrifos"]/3), 
                   yend = unique(Final.Data$Single.C.HC5.bf[Final.Data$Chemical == "Chlorpyrifos"]/3)),
               colour = "black", linetype = "dotted")+ # add in 3 fold lower for Chlorpyrifos
  geom_segment(aes(x = 2.5, xend = 3.5, 
                   y = unique(Final.Data$Single.C.HC5.bf[Final.Data$Chemical == "Malathion"]*5), 
                   yend = unique(Final.Data$Single.C.HC5.bf[Final.Data$Chemical == "Malathion"]*5)),
               colour = "black", linetype = "dashed")+ # add in 5 fold upper for Malathion
  geom_segment(aes(x = 2.5, xend = 3.5, 
                   y = unique(Final.Data$Single.C.HC5.bf[Final.Data$Chemical == "Malathion"]/5), 
                   yend = unique(Final.Data$Single.C.HC5.bf[Final.Data$Chemical == "Malathion"]/5)),
               colour = "black", linetype = "dashed")+ # add in 5 fold lower for Malathion
  geom_segment(aes(x = 2.5, xend = 3.5, 
                   y = unique(Final.Data$Single.C.HC5.bf[Final.Data$Chemical == "Malathion"]*3), 
                   yend = unique(Final.Data$Single.C.HC5.bf[Final.Data$Chemical == "Malathion"]*3)),
               colour = "black", linetype = "dotted")+ # add in 3 fold upper for Malathion
  geom_segment(aes(x = 2.5, xend = 3.5, 
                   y = unique(Final.Data$Single.C.HC5.bf[Final.Data$Chemical == "Malathion"]/3), 
                   yend = unique(Final.Data$Single.C.HC5.bf[Final.Data$Chemical == "Malathion"]/3)),
               colour = "black", linetype = "dotted")+ # add in 3 fold upper for Malathion
  geom_segment(aes(x = 3.5, xend = 4.5, 
                   y = unique(Final.Data$Single.C.HC5.bf[Final.Data$Chemical == "EPN"]*5), 
                   yend = unique(Final.Data$Single.C.HC5.bf[Final.Data$Chemical == "EPN"]*5)),
               colour = "black", linetype = "dashed")+ # add in 5 fold upper for EPN
  geom_segment(aes(x = 3.5, xend = 4.5, 
                   y = unique(Final.Data$Single.C.HC5.bf[Final.Data$Chemical == "EPN"]/5), 
                   yend = unique(Final.Data$Single.C.HC5.bf[Final.Data$Chemical == "EPN"]/5)),
               colour = "black", linetype = "dashed")+ # add in 5 fold lower for EPN
  geom_segment(aes(x = 3.5, xend = 4.5, 
                   y = unique(Final.Data$Single.C.HC5.bf[Final.Data$Chemical == "EPN"]*3), 
                   yend = unique(Final.Data$Single.C.HC5.bf[Final.Data$Chemical == "EPN"]*3)),
               colour = "black", linetype = "dotted")+ # add in 3 fold upper for EPN
  geom_segment(aes(x = 3.5, xend = 4.5, 
                   y = unique(Final.Data$Single.C.HC5.bf[Final.Data$Chemical == "EPN"]/3), 
                   yend = unique(Final.Data$Single.C.HC5.bf[Final.Data$Chemical == "EPN"]/3)),
               colour = "black", linetype = "dotted")+ # add in 3 fold lower for EPN
  geom_segment(aes(x = 4.5, xend = 5.5, 
                   y = unique(Final.Data$Single.C.HC5.bf[Final.Data$Chemical == "Disulfoton"]*5), 
                   yend = unique(Final.Data$Single.C.HC5.bf[Final.Data$Chemical == "Disulfoton"]*5)),
               colour = "black", linetype = "dashed")+ # add in 5 fold upper for Disulfoton
  geom_segment(aes(x = 4.5, xend = 5.5, 
                   y = unique(Final.Data$Single.C.HC5.bf[Final.Data$Chemical == "Disulfoton"]/5), 
                   yend = unique(Final.Data$Single.C.HC5.bf[Final.Data$Chemical == "Disulfoton"]/5)),
               colour = "black", linetype = "dashed")+ # add in 5 fold lower for Disulfoton
  geom_segment(aes(x = 4.5, xend = 5.5, 
                   y = unique(Final.Data$Single.C.HC5.bf[Final.Data$Chemical == "Disulfoton"]*3), 
                   yend = unique(Final.Data$Single.C.HC5.bf[Final.Data$Chemical == "Disulfoton"]*3)),
               colour = "black", linetype = "dotted")+ # add in 3 fold upper for Disulfoton
  geom_segment(aes(x = 4.5, xend = 5.5, 
                   y = unique(Final.Data$Single.C.HC5.bf[Final.Data$Chemical == "Disulfoton"]/3), 
                   yend = unique(Final.Data$Single.C.HC5.bf[Final.Data$Chemical == "Disulfoton"]/3)),
               colour = "black", linetype = "dotted")+ # add in 3 fold lower for Disulfoton
  geom_segment(aes(x = 5.5, xend = 6.5, 
                   y = unique(Final.Data$Single.C.HC5.bf[Final.Data$Chemical == "Dichlorvos"]*5), 
                   yend = unique(Final.Data$Single.C.HC5.bf[Final.Data$Chemical == "Dichlorvos"]*5)),
               colour = "black", linetype = "dashed")+ # add in 5 fold upper for Dichlorvos
  geom_segment(aes(x = 5.5, xend = 6.5, 
                   y = unique(Final.Data$Single.C.HC5.bf[Final.Data$Chemical == "Dichlorvos"]/5), 
                   yend = unique(Final.Data$Single.C.HC5.bf[Final.Data$Chemical == "Dichlorvos"]/5)),
               colour = "black", linetype = "dashed")+ # add in 5 fold lower for Dichlorvos
  geom_segment(aes(x = 5.5, xend = 6.5, 
                   y = unique(Final.Data$Single.C.HC5.bf[Final.Data$Chemical == "Dichlorvos"]*3), 
                   yend = unique(Final.Data$Single.C.HC5.bf[Final.Data$Chemical == "Dichlorvos"]*3)),
               colour = "black", linetype = "dotted")+ # add in 3 fold upper for Dichlorvos
  geom_segment(aes(x = 5.5, xend = 6.5, 
                   y = unique(Final.Data$Single.C.HC5.bf[Final.Data$Chemical == "Dichlorvos"]/3), 
                   yend = unique(Final.Data$Single.C.HC5.bf[Final.Data$Chemical == "Dichlorvos"]/3)),
               colour = "black", linetype = "dotted")+ # add in 3 fold lower for Dichlorvos
  theme_bw()+ # black and white theme
  ylab(expression(bold(paste("HC5 (", mu, "g/L)"))))+ # add y axis label
  scale_y_log10()+
  scale_color_manual(values = comp.plot.colours)+ # set colours to the colour palette I chose
  scale_shape_manual(values = comp.plot.shapes)+ # set shapes to ones i chose
  scale_x_discrete(expand = c(0, 0.5))+ # cut off the left and right edge of the graph so all boxes are same size
  theme(axis.text.x = element_text(face = "bold", angle = 45, hjust = 1, size = 13, colour = "black"), # rotate labels 45 degrees for reading, make font 11 point
        axis.title.x = element_blank(), # remove x axis label
        axis.title.y = element_text(face = "bold", size = 14, margin = margin(r = 20)),
        axis.text.y = element_text(face = "bold", size = 13, colour = "black"),
        legend.text = element_text(face = "bold", size = 13, colour = "black"),
        legend.title = element_text(face = "bold", size = 13))
comp.plot.1
```


### Make the second plot
```{r}

# Make test data frame
plot.2.data <- long.data.total
  
plot.2.data <- plot.2.data %>%
  filter(
    Chemical == "Parathion" | Chemical == "Trichlorfon" | Chemical ==  "Diazinon" | Chemical == "Coumaphos" | Chemical ==  "Fenthion" | Chemical ==  "Methyl parathion" | Chemical == "Fenitrothion"
  )

# make method a factor with these levels to match the plot
plot.2.data$Method <- factor(plot.2.data$Method, levels = c("SSD", "LOO", "SSDn"))

# manually change the factor levels of the chemicals so that it goes in order from smallest HC5 to largest HC5
plot.2.data$Chemical <- factor(plot.2.data$Chemical, levels = c("Parathion", "Trichlorfon", "Diazinon","Coumaphos", "Fenthion", "Methyl parathion","Fenitrothion"))

```


### Comparison plot including the single-chemical HC5 as well
This plot has three values, the LOO HC5 mean and CI, the single-chemical HC5, and the SSDn HC5 mean and CI.
```{r}
# first make long data a factor so it can be plotted
plot.2.data$Method <- as.factor(plot.2.data$Method)


# set up color palette
comp.plot.colours <- c(SSD = "#000000", LOO = "#000000", SSDn = "#000000") # color palette (all black)
comp.plot.shapes <- c(SSD = 17, LOO = 19, SSDn = 15) # shape types


# Create a comparison plot
comp.plot.2 <- plot.2.data %>%
  ggplot()+
  aes(x = Chemical, y = HC5.Mean.Estimate, ymin = HC5.Lower.CI, ymax = HC5.Upper.CI, color = Method, shape = Method)+
  geom_point(size = 2.5, position = position_dodge(width = 1))+ # add in the points, dodge so they don't hit or overlap each other
  geom_linerange(aes(ymax= HC5.Upper.CI, ymin = pmax(HC5.Lower.CI, 0)), size = 1, position = position_dodge(width = 1))+ # set line ranges as the upper and lower CIs
  geom_vline(xintercept = 1.5)+ # add in vertical line to separate chemicals
  geom_vline(xintercept = 2.5)+ # add in vertical line to separate chemicals
  geom_vline(xintercept = 3.5)+ # add in vertical line to separate chemicals
  geom_vline(xintercept = 4.5)+ # add in vertical line to separate chemicals
  geom_vline(xintercept = 5.5)+ # add in vertical line to separate chemicals
  geom_vline(xintercept = 6.5)+ # add in vertical line to separate chemicals
  geom_segment(aes(x = 0.5, xend = 1.5, 
                   y = unique(Final.Data$Single.C.HC5.bf[Final.Data$Chemical == "Parathion"]*5), 
                   yend = unique(Final.Data$Single.C.HC5.bf[Final.Data$Chemical == "Parathion"]*5)),
               colour = "black", linetype = "dashed")+ # add in 5 fold upper for Parathion
  geom_segment(aes(x = 0.5, xend = 1.5, 
                   y = unique(Final.Data$Single.C.HC5.bf[Final.Data$Chemical == "Parathion"]/5), 
                   yend = unique(Final.Data$Single.C.HC5.bf[Final.Data$Chemical == "Parathion"]/5)),
               colour = "black", linetype = "dashed")+ # add in 5 fold lower for Parathion
  geom_segment(aes(x = 0.5, xend = 1.5, 
                   y = unique(Final.Data$Single.C.HC5.bf[Final.Data$Chemical == "Parathion"]*3), 
                   yend = unique(Final.Data$Single.C.HC5.bf[Final.Data$Chemical == "Parathion"]*3)),
               colour = "black", linetype = "dotted")+ # add in 3 fold upper for Parathion
  geom_segment(aes(x = 0.5, xend = 1.5, 
                   y = unique(Final.Data$Single.C.HC5.bf[Final.Data$Chemical == "Parathion"]/3), 
                   yend = unique(Final.Data$Single.C.HC5.bf[Final.Data$Chemical == "Parathion"]/3)),
               colour = "black", linetype = "dotted")+ # add in 3 fold lower for Parathion
  geom_segment(aes(x = 1.5, xend = 2.5, 
                   y = unique(Final.Data$Single.C.HC5.bf[Final.Data$Chemical == "Trichlorfon"]*5), 
                   yend = unique(Final.Data$Single.C.HC5.bf[Final.Data$Chemical == "Trichlorfon"]*5)),
               colour = "black", linetype = "dashed")+ # add in 5 fold upper for Trichlorfon
  geom_segment(aes(x = 1.5, xend = 2.5, 
                   y = unique(Final.Data$Single.C.HC5.bf[Final.Data$Chemical == "Trichlorfon"]/5), 
                   yend = unique(Final.Data$Single.C.HC5.bf[Final.Data$Chemical == "Trichlorfon"]/5)),
               colour = "black", linetype = "dashed")+ # add in 5 fold lower for Trichlorfon
  geom_segment(aes(x = 1.5, xend = 2.5, 
                   y = unique(Final.Data$Single.C.HC5.bf[Final.Data$Chemical == "Trichlorfon"]*3), 
                   yend = unique(Final.Data$Single.C.HC5.bf[Final.Data$Chemical == "Trichlorfon"]*3)),
               colour = "black", linetype = "dotted")+ # add in 3 fold upper for Trichlorfon
  geom_segment(aes(x = 1.5, xend = 2.5, 
                   y = unique(Final.Data$Single.C.HC5.bf[Final.Data$Chemical == "Trichlorfon"]/3), 
                   yend = unique(Final.Data$Single.C.HC5.bf[Final.Data$Chemical == "Trichlorfon"]/3)),
               colour = "black", linetype = "dotted")+ # add in 3 fold lower for Trichlorfon
  geom_segment(aes(x = 2.5, xend = 3.5, 
                   y = unique(Final.Data$Single.C.HC5.bf[Final.Data$Chemical == "Diazinon"]*5), 
                   yend = unique(Final.Data$Single.C.HC5.bf[Final.Data$Chemical == "Diazinon"]*5)),
               colour = "black", linetype = "dashed")+ # add in 5 fold upper for Diazinon
  geom_segment(aes(x = 2.5, xend = 3.5, 
                   y = unique(Final.Data$Single.C.HC5.bf[Final.Data$Chemical == "Diazinon"]/5), 
                   yend = unique(Final.Data$Single.C.HC5.bf[Final.Data$Chemical == "Diazinon"]/5)),
               colour = "black", linetype = "dashed")+ # add in 5 fold lower for Diazinon
  geom_segment(aes(x = 2.5, xend = 3.5, 
                   y = unique(Final.Data$Single.C.HC5.bf[Final.Data$Chemical == "Diazinon"]*3), 
                   yend = unique(Final.Data$Single.C.HC5.bf[Final.Data$Chemical == "Diazinon"]*3)),
               colour = "black", linetype = "dotted")+ # add in 3 fold upper for Diazinon
  geom_segment(aes(x = 2.5, xend = 3.5, 
                   y = unique(Final.Data$Single.C.HC5.bf[Final.Data$Chemical == "Diazinon"]/3), 
                   yend = unique(Final.Data$Single.C.HC5.bf[Final.Data$Chemical == "Diazinon"]/3)),
               colour = "black", linetype = "dotted")+ # add in 3 fold upper for Diazinon
  geom_segment(aes(x = 3.5, xend = 4.5, 
                   y = unique(Final.Data$Single.C.HC5.bf[Final.Data$Chemical == "Coumaphos"]*5), 
                   yend = unique(Final.Data$Single.C.HC5.bf[Final.Data$Chemical == "Coumaphos"]*5)),
               colour = "black", linetype = "dashed")+ # add in 5 fold upper for Coumaphos
  geom_segment(aes(x = 3.5, xend = 4.5, 
                   y = unique(Final.Data$Single.C.HC5.bf[Final.Data$Chemical == "Coumaphos"]/5), 
                   yend = unique(Final.Data$Single.C.HC5.bf[Final.Data$Chemical == "Coumaphos"]/5)),
               colour = "black", linetype = "dashed")+ # add in 5 fold lower for Coumaphos
  geom_segment(aes(x = 3.5, xend = 4.5, 
                   y = unique(Final.Data$Single.C.HC5.bf[Final.Data$Chemical == "Coumaphos"]*3), 
                   yend = unique(Final.Data$Single.C.HC5.bf[Final.Data$Chemical == "Coumaphos"]*3)),
               colour = "black", linetype = "dotted")+ # add in 3 fold upper for Coumaphos
  geom_segment(aes(x = 3.5, xend = 4.5, 
                   y = unique(Final.Data$Single.C.HC5.bf[Final.Data$Chemical == "Coumaphos"]/3), 
                   yend = unique(Final.Data$Single.C.HC5.bf[Final.Data$Chemical == "Coumaphos"]/3)),
               colour = "black", linetype = "dotted")+ # add in 3 fold lower for Coumaphos
  geom_segment(aes(x = 4.5, xend = 5.5, 
                   y = unique(Final.Data$Single.C.HC5.bf[Final.Data$Chemical == "Fenthion"]*5), 
                   yend = unique(Final.Data$Single.C.HC5.bf[Final.Data$Chemical == "Fenthion"]*5)),
               colour = "black", linetype = "dashed")+ # add in 5 fold upper for Fenthion
  geom_segment(aes(x = 4.5, xend = 5.5, 
                   y = unique(Final.Data$Single.C.HC5.bf[Final.Data$Chemical == "Fenthion"]/5), 
                   yend = unique(Final.Data$Single.C.HC5.bf[Final.Data$Chemical == "Fenthion"]/5)),
               colour = "black", linetype = "dashed")+ # add in 5 fold lower for Fenthion
  geom_segment(aes(x = 4.5, xend = 5.5, 
                   y = unique(Final.Data$Single.C.HC5.bf[Final.Data$Chemical == "Fenthion"]*3), 
                   yend = unique(Final.Data$Single.C.HC5.bf[Final.Data$Chemical == "Fenthion"]*3)),
               colour = "black", linetype = "dotted")+ # add in 3 fold upper for Fenthion
  geom_segment(aes(x = 4.5, xend = 5.5, 
                   y = unique(Final.Data$Single.C.HC5.bf[Final.Data$Chemical == "Fenthion"]/3), 
                   yend = unique(Final.Data$Single.C.HC5.bf[Final.Data$Chemical == "Fenthion"]/3)),
               colour = "black", linetype = "dotted")+ # add in 3 fold lower for Fenthion
  geom_segment(aes(x = 5.5, xend = 6.5, 
                   y = unique(Final.Data$Single.C.HC5.bf[Final.Data$Chemical == "Methyl parathion"]*5), 
                   yend = unique(Final.Data$Single.C.HC5.bf[Final.Data$Chemical == "Methyl parathion"]*5)),
               colour = "black", linetype = "dashed")+ # add in 5 fold upper for Methyl parathion
  geom_segment(aes(x = 5.5, xend = 6.5, 
                   y = unique(Final.Data$Single.C.HC5.bf[Final.Data$Chemical == "Methyl parathion"]/5), 
                   yend = unique(Final.Data$Single.C.HC5.bf[Final.Data$Chemical == "Methyl parathion"]/5)),
               colour = "black", linetype = "dashed")+ # add in 5 fold lower for Methyl parathion
  geom_segment(aes(x = 5.5, xend = 6.5, 
                   y = unique(Final.Data$Single.C.HC5.bf[Final.Data$Chemical == "Methyl parathion"]*3), 
                   yend = unique(Final.Data$Single.C.HC5.bf[Final.Data$Chemical == "Methyl parathion"]*3)),
               colour = "black", linetype = "dotted")+ # add in 3 fold upper for Methyl parathion
  geom_segment(aes(x = 5.5, xend = 6.5, 
                   y = unique(Final.Data$Single.C.HC5.bf[Final.Data$Chemical == "Methyl parathion"]/3), 
                   yend = unique(Final.Data$Single.C.HC5.bf[Final.Data$Chemical == "Methyl parathion"]/3)),
               colour = "black", linetype = "dotted")+ # add in 3 fold lower for Methyl parathion
  geom_segment(aes(x = 6.5, xend = 7.5, 
                   y = unique(Final.Data$Single.C.HC5.bf[Final.Data$Chemical == "Fenitrothion"]*5), 
                   yend = unique(Final.Data$Single.C.HC5.bf[Final.Data$Chemical == "Fenitrothion"]*5)),
               colour = "black", linetype = "dashed")+ # add in 5 fold upper for Fenitrothion
  geom_segment(aes(x = 6.5, xend = 7.5, 
                   y = unique(Final.Data$Single.C.HC5.bf[Final.Data$Chemical == "Fenitrothion"]/5), 
                   yend = unique(Final.Data$Single.C.HC5.bf[Final.Data$Chemical == "Fenitrothion"]/5)),
               colour = "black", linetype = "dashed")+ # add in 5 fold lower for Fenitrothion
  geom_segment(aes(x = 6.5, xend = 7.5, 
                   y = unique(Final.Data$Single.C.HC5.bf[Final.Data$Chemical == "Fenitrothion"]*3), 
                   yend = unique(Final.Data$Single.C.HC5.bf[Final.Data$Chemical == "Fenitrothion"]*3)),
               colour = "black", linetype = "dotted")+ # add in 3 fold upper for Fenitrothion
  geom_segment(aes(x = 6.5, xend = 7.5, 
                   y = unique(Final.Data$Single.C.HC5.bf[Final.Data$Chemical == "Fenitrothion"]/3), 
                   yend = unique(Final.Data$Single.C.HC5.bf[Final.Data$Chemical == "Fenitrothion"]/3)),
               colour = "black", linetype = "dotted")+ # add in 3 fold lower for Fenitrothion
  theme_bw()+ # black and white theme
  ylab(expression(bold(paste("HC5 (", mu, "g/L)"))))+ # add y axis label
  scale_y_log10()+
  scale_color_manual(values = comp.plot.colours)+ # set colours to the colour palette I chose
  scale_shape_manual(values = comp.plot.shapes)+ # set shapes to ones i chose
  scale_x_discrete(expand = c(0, 0.5))+ # cut off the left and right edge of the graph so all boxes are same size
  theme(axis.text.x = element_text(face = "bold", angle = 45, hjust = 1, size = 13, colour = "black"), # rotate labels 45 degrees for reading, make font 11 point
        axis.title.x = element_blank(), # remove x axis label
        axis.title.y = element_text(face = "bold", size = 14, margin = margin(r = 20)),
        axis.text.y = element_text(face = "bold", size = 13, colour = "black"),
        legend.text = element_text(face = "bold", size = 13, colour = "black"),
        legend.title = element_text(face = "bold", size = 13))
comp.plot.2
```

## Individual Chemical Plotting

### Chemical 1: Azinphos-methyl

#### Plot 1: Raw SSDn Output plot
The chunk below filters the data only for Azinphos-methyl, then plots the raw output of all the SSDn results. The plot shows that overall, most nSpecies under-estimated the HC5 compared to the "true" HC5.
```{r}
# Filter the data to only include Azinphos-methyl
Azinphos.methyl <- Final.Data %>%
  filter(
    Chemical == "Azinphos-methyl"
  )

# Arrange the nSpecies by the toxicity value (so the most sensitive species are at the top)
Azinphos.methyl <- Azinphos.methyl %>%
   arrange(average, nSpecies)

# Extract the order of the species and check
Azinphos.methyl.n.spec <- unique(Azinphos.methyl$nSpecies)
Azinphos.methyl.n.spec

# Relevel the factors to match the order
Azinphos.methyl$nSpecies <- factor(Azinphos.methyl$nSpecies, levels = Azinphos.methyl.n.spec)
       
# Create the plot
Azinphos.methyl.plot <- ggplot(Azinphos.methyl, aes(x = nSpecies, y = bf.HC5))+ # X axis is the nSpecies, Y axis is the back-calculated HC5s that were generated from SSDs that used the nSpecies
  geom_point(position = position_dodge(width = 0.5))+ # add in the points
  geom_hline(yintercept = Azinphos.methyl$Single.C.HC5.bf, colour = "red")+ # Add the "true" HC5 as a red line across
  geom_hline(yintercept = (Azinphos.methyl$Single.C.HC5.bf*5), colour = "red", linetype = 2)+ # Add the 5-fold higher mark as a dashed red line
  geom_hline(yintercept = (Azinphos.methyl$Single.C.HC5.bf/5), colour = "red", linetype = 2)+ # Add the 5-fold lower mark as a dashed red line
  geom_vline(xintercept = 3.5, linetype = 2)+ # Designate the first quartile to the left of the line
  theme_bw()+ # black and white theme
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+ # rotate x axis labels 45 degrees for reading
  scale_y_log10()+ # make whole graph log scale
  xlab("nSpecies")+
  ylab("HC5 (ug/L)")+
  ggtitle("Azinphos-methyl SSDn Estimated HC5s (FISH ONLY)") # add title
Azinphos.methyl.plot
```



### Chemical 2: Chlorpyrifos

#### Plot 1: Raw SSDn Output plot
The chunk below filters the data only for Chlorpyrifos, then plots the raw output of all the SSDn results. The plot shows that overall, most nSpecies under-estimated the HC5 compared to the "true" HC5.
```{r}
# Filter the data to only include Chlorpyrifos
Chlorpyrifos <- Final.Data %>%
  filter(
    Chemical == "Chlorpyrifos"
  )

# Arrange the nSpecies by the toxicity value (so the most sensitive species are at the top)
Chlorpyrifos <- Chlorpyrifos %>%
   arrange(average, nSpecies)

# Extract the order of the species and check
Chlorpyrifos.n.spec <- unique(Chlorpyrifos$nSpecies)
Chlorpyrifos.n.spec

# Relevel the factors to match the order
Chlorpyrifos$nSpecies <- factor(Chlorpyrifos$nSpecies, levels = Chlorpyrifos.n.spec)
       
# Create the plot
Chlorpyrifos.plot <- ggplot(Chlorpyrifos, aes(x = nSpecies, y = bf.HC5))+ # X axis is the nSpecies, Y axis is the back-calculated HC5s that were generated from SSDs that used the nSpecies
  geom_point(position = position_dodge(width = 0.5))+ # add in the points
  geom_hline(yintercept = Chlorpyrifos$Single.C.HC5.bf, colour = "red")+ # Add the "true" HC5 as a red line across
  geom_hline(yintercept = (Chlorpyrifos$Single.C.HC5.bf*5), colour = "red", linetype = 2)+ # Add the 5-fold higher mark as a dashed red line
  geom_hline(yintercept = (Chlorpyrifos$Single.C.HC5.bf/5), colour = "red", linetype = 2)+ # Add the 5-fold lower mark as a dashed red line
  geom_vline(xintercept = 3.5, linetype = 2)+ # Designate the first quartile to the left of the line
  theme_bw()+ # black and white theme
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+ # rotate x axis labels 45 degrees for reading
  scale_y_log10()+ # make whole graph log scale
  xlab("nSpecies")+
  ylab("HC5 (ug/L)")+
  ggtitle("Chlorpyrifos SSDn Estimated HC5s (FISH ONLY)") # add title
Chlorpyrifos.plot
```





### Chemical 3: Coumaphos

#### Plot 1: Raw SSDn Output plot
The chunk below filters the data only for Coumaphos, then plots the raw output of all the SSDn results. The plot shows that overall, most nSpecies under-estimated the HC5 compared to the "true" HC5.
```{r}
# Filter the data to only include Coumaphos
Coumaphos <- Final.Data %>%
  filter(
    Chemical == "Coumaphos"
  )

# Arrange the nSpecies by the toxicity value (so the most sensitive species are at the top)
Coumaphos <- Coumaphos %>%
   arrange(average, nSpecies)

# Extract the order of the species and check
Coumaphos.n.spec <- unique(Coumaphos$nSpecies)
Coumaphos.n.spec

# Relevel the factors to match the order
Coumaphos$nSpecies <- factor(Coumaphos$nSpecies, levels = Coumaphos.n.spec)
       
# Create the plot
Coumaphos.plot <- ggplot(Coumaphos, aes(x = nSpecies, y = bf.HC5))+ # X axis is the nSpecies, Y axis is the back-calculated HC5s that were generated from SSDs that used the nSpecies
  geom_point(position = position_dodge(width = 0.5))+ # add in the points
  geom_hline(yintercept = Coumaphos$Single.C.HC5.bf, colour = "red")+ # Add the "true" HC5 as a red line across
  geom_hline(yintercept = (Coumaphos$Single.C.HC5.bf*5), colour = "red", linetype = 2)+ # Add the 5-fold higher mark as a dashed red line
  geom_hline(yintercept = (Coumaphos$Single.C.HC5.bf/5), colour = "red", linetype = 2)+ # Add the 5-fold lower mark as a dashed red line
  geom_vline(xintercept = 3.5, linetype = 2)+ # Designate the first quartile to the left of the line
  theme_bw()+ # black and white theme
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+ # rotate x axis labels 45 degrees for reading
  scale_y_log10()+ # make whole graph log scale
  xlab("nSpecies")+
  ylab("HC5 (ug/L)")+
  ggtitle("Coumaphos SSDn Estimated HC5s (FISH ONLY)") # add title
Coumaphos.plot
```




### Chemical 4: Diazinon

#### Plot 1: Raw SSDn Output plot
The chunk below filters the data only for Diazinon, then plots the raw output of all the SSDn results. The plot shows that overall, most nSpecies under-estimated the HC5 compared to the "true" HC5.
```{r}
# Filter the data to only include Diazinon
Diazinon <- Final.Data %>%
  filter(
    Chemical == "Diazinon"
  )

# Arrange the nSpecies by the toxicity value (so the most sensitive species are at the top)
Diazinon <- Diazinon %>%
   arrange(average, nSpecies)

# Extract the order of the species and check
Diazinon.n.spec <- unique(Diazinon$nSpecies)
Diazinon.n.spec

# Relevel the factors to match the order
Diazinon$nSpecies <- factor(Diazinon$nSpecies, levels = Diazinon.n.spec)
       
# Create the plot
Diazinon.plot <- ggplot(Diazinon, aes(x = nSpecies, y = bf.HC5))+ # X axis is the nSpecies, Y axis is the back-calculated HC5s that were generated from SSDs that used the nSpecies
  geom_point(position = position_dodge(width = 0.5))+ # add in the points
  geom_hline(yintercept = Diazinon$Single.C.HC5.bf, colour = "red")+ # Add the "true" HC5 as a red line across
  geom_hline(yintercept = (Diazinon$Single.C.HC5.bf*5), colour = "red", linetype = 2)+ # Add the 5-fold higher mark as a dashed red line
  geom_hline(yintercept = (Diazinon$Single.C.HC5.bf/5), colour = "red", linetype = 2)+ # Add the 5-fold lower mark as a dashed red line
  geom_vline(xintercept = 3.5, linetype = 2)+ # Designate the first quartile to the left of the line
  theme_bw()+ # black and white theme
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+ # rotate x axis labels 45 degrees for reading
  scale_y_log10()+ # make whole graph log scale
  xlab("nSpecies")+
  ylab("HC5 (ug/L)")+
  ggtitle("Diazinon SSDn Estimated HC5s (FISH ONLY)") # add title
Diazinon.plot
```



### Chemical 5: Dichlorvos

#### Plot 1: Raw SSDn Output plot
The chunk below filters the data only for Dichlorvos, then plots the raw output of all the SSDn results. The plot shows that overall, most nSpecies under-estimated the HC5 compared to the "true" HC5.
```{r}
# Filter the data to only include Dichlorvos
Dichlorvos <- Final.Data %>%
  filter(
    Chemical == "Dichlorvos"
  )

# Arrange the nSpecies by the toxicity value (so the most sensitive species are at the top)
Dichlorvos <- Dichlorvos %>%
   arrange(average, nSpecies)

# Extract the order of the species and check
Dichlorvos.n.spec <- unique(Dichlorvos$nSpecies)
Dichlorvos.n.spec

# Relevel the factors to match the order
Dichlorvos$nSpecies <- factor(Dichlorvos$nSpecies, levels = Dichlorvos.n.spec)
       
# Create the plot
Dichlorvos.plot <- ggplot(Dichlorvos, aes(x = nSpecies, y = bf.HC5))+ # X axis is the nSpecies, Y axis is the back-calculated HC5s that were generated from SSDs that used the nSpecies
  geom_point(position = position_dodge(width = 0.5))+ # add in the points
  geom_hline(yintercept = Dichlorvos$Single.C.HC5.bf, colour = "red")+ # Add the "true" HC5 as a red line across
  geom_hline(yintercept = (Dichlorvos$Single.C.HC5.bf*5), colour = "red", linetype = 2)+ # Add the 5-fold higher mark as a dashed red line
  geom_hline(yintercept = (Dichlorvos$Single.C.HC5.bf/5), colour = "red", linetype = 2)+ # Add the 5-fold lower mark as a dashed red line
  geom_vline(xintercept = 3.5, linetype = 2)+ # Designate the first quartile to the left of the line
  theme_bw()+ # black and white theme
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+ # rotate x axis labels 45 degrees for reading
  scale_y_log10()+ # make whole graph log scale
  xlab("nSpecies")+
  ylab("HC5 (ug/L)")+
  ggtitle("Dichlorvos SSDn Estimated HC5s (FISH ONLY)") # add title
Dichlorvos.plot
```



### Chemical 6: Disulfoton

#### Plot 1: Raw SSDn Output plot
The chunk below filters the data only for Disulfoton, then plots the raw output of all the SSDn results. The plot shows that overall, most nSpecies under-estimated the HC5 compared to the "true" HC5.
```{r}
# Filter the data to only include Disulfoton
Disulfoton <- Final.Data %>%
  filter(
    Chemical == "Disulfoton"
  )

# Arrange the nSpecies by the toxicity value (so the most sensitive species are at the top)
Disulfoton <- Disulfoton %>%
   arrange(average, nSpecies)

# Extract the order of the species and check
Disulfoton.n.spec <- unique(Disulfoton$nSpecies)
Disulfoton.n.spec

# Relevel the factors to match the order
Disulfoton$nSpecies <- factor(Disulfoton$nSpecies, levels = Disulfoton.n.spec)
       
# Create the plot
Disulfoton.plot <- ggplot(Disulfoton, aes(x = nSpecies, y = bf.HC5))+ # X axis is the nSpecies, Y axis is the back-calculated HC5s that were generated from SSDs that used the nSpecies
  geom_point(position = position_dodge(width = 0.5))+ # add in the points
  geom_hline(yintercept = Disulfoton$Single.C.HC5.bf, colour = "red")+ # Add the "true" HC5 as a red line across
  geom_hline(yintercept = (Disulfoton$Single.C.HC5.bf*5), colour = "red", linetype = 2)+ # Add the 5-fold higher mark as a dashed red line
  geom_hline(yintercept = (Disulfoton$Single.C.HC5.bf/5), colour = "red", linetype = 2)+ # Add the 5-fold lower mark as a dashed red line
  geom_vline(xintercept = 3.5, linetype = 2)+ # Designate the first quartile to the left of the line
  theme_bw()+ # black and white theme
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+ # rotate x axis labels 45 degrees for reading
  scale_y_log10()+ # make whole graph log scale
  xlab("nSpecies")+
  ylab("HC5 (ug/L)")+
  ggtitle("Disulfoton SSDn Estimated HC5s (FISH ONLY)") # add title
Disulfoton.plot
```




### Chemical 7: EPN

#### Plot 1: Raw SSDn Output plot
The chunk below filters the data only for EPN, then plots the raw output of all the SSDn results. The plot shows that overall, most nSpecies under-estimated the HC5 compared to the "true" HC5.
```{r}
# Filter the data to only include EPN
EPN <- Final.Data %>%
  filter(
    Chemical == "EPN"
  )

# Arrange the nSpecies by the toxicity value (so the most sensitive species are at the top)
EPN <- EPN %>%
   arrange(average, nSpecies)

# Extract the order of the species and check
EPN.n.spec <- unique(EPN$nSpecies)
EPN.n.spec

# Relevel the factors to match the order
EPN$nSpecies <- factor(EPN$nSpecies, levels = EPN.n.spec)
       
# Create the plot
EPN.plot <- ggplot(EPN, aes(x = nSpecies, y = bf.HC5))+ # X axis is the nSpecies, Y axis is the back-calculated HC5s that were generated from SSDs that used the nSpecies
  geom_point(position = position_dodge(width = 0.5))+ # add in the points
  geom_hline(yintercept = EPN$Single.C.HC5.bf, colour = "red")+ # Add the "true" HC5 as a red line across
  geom_hline(yintercept = (EPN$Single.C.HC5.bf*5), colour = "red", linetype = 2)+ # Add the 5-fold higher mark as a dashed red line
  geom_hline(yintercept = (EPN$Single.C.HC5.bf/5), colour = "red", linetype = 2)+ # Add the 5-fold lower mark as a dashed red line
  geom_vline(xintercept = 3.5, linetype = 2)+ # Designate the first quartile to the left of the line
  theme_bw()+ # black and white theme
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+ # rotate x axis labels 45 degrees for reading
  scale_y_log10()+ # make whole graph log scale
  xlab("nSpecies")+
  ylab("HC5 (ug/L)")+
  ggtitle("EPN SSDn Estimated HC5s (FISH ONLY)") # add title
EPN.plot
```



### Chemical 8: Fenitrothion

#### Plot 1: Raw SSDn Output plot
The chunk below filters the data only for Fenitrothion, then plots the raw output of all the SSDn results. The plot shows that overall, most nSpecies under-estimated the HC5 compared to the "true" HC5.
```{r}
# Filter the data to only include Fenitrothion
Fenitrothion <- Final.Data %>%
  filter(
    Chemical == "Fenitrothion"
  )

# Arrange the nSpecies by the toxicity value (so the most sensitive species are at the top)
Fenitrothion <- Fenitrothion %>%
   arrange(average, nSpecies)

# Extract the order of the species and check
Fenitrothion.n.spec <- unique(Fenitrothion$nSpecies)
Fenitrothion.n.spec

# Relevel the factors to match the order
Fenitrothion$nSpecies <- factor(Fenitrothion$nSpecies, levels = Fenitrothion.n.spec)
       
# Create the plot
Fenitrothion.plot <- ggplot(Fenitrothion, aes(x = nSpecies, y = bf.HC5))+ # X axis is the nSpecies, Y axis is the back-calculated HC5s that were generated from SSDs that used the nSpecies
  geom_point(position = position_dodge(width = 0.5))+ # add in the points
  geom_hline(yintercept = Fenitrothion$Single.C.HC5.bf, colour = "red")+ # Add the "true" HC5 as a red line across
  geom_hline(yintercept = (Fenitrothion$Single.C.HC5.bf*5), colour = "red", linetype = 2)+ # Add the 5-fold higher mark as a dashed red line
  geom_hline(yintercept = (Fenitrothion$Single.C.HC5.bf/5), colour = "red", linetype = 2)+ # Add the 5-fold lower mark as a dashed red line
  geom_vline(xintercept = 3.5, linetype = 2)+ # Designate the first quartile to the left of the line
  theme_bw()+ # black and white theme
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+ # rotate x axis labels 45 degrees for reading
  scale_y_log10()+ # make whole graph log scale
  xlab("nSpecies")+
  ylab("HC5 (ug/L)")+
  ggtitle("Fenitrothion SSDn Estimated HC5s (FISH ONLY)") # add title
Fenitrothion.plot
```



### Chemical 9: Fenthion

#### Plot 1: Raw SSDn Output plot
The chunk below filters the data only for Fenthion, then plots the raw output of all the SSDn results. The plot shows that overall, most nSpecies under-estimated the HC5 compared to the "true" HC5.
```{r}
# Filter the data to only include Fenthion
Fenthion <- Final.Data %>%
  filter(
    Chemical == "Fenthion"
  )

# Arrange the nSpecies by the toxicity value (so the most sensitive species are at the top)
Fenthion <- Fenthion %>%
   arrange(average, nSpecies)

# Extract the order of the species and check
Fenthion.n.spec <- unique(Fenthion$nSpecies)
Fenthion.n.spec

# Relevel the factors to match the order
Fenthion$nSpecies <- factor(Fenthion$nSpecies, levels = Fenthion.n.spec)
       
# Create the plot
Fenthion.plot <- ggplot(Fenthion, aes(x = nSpecies, y = bf.HC5))+ # X axis is the nSpecies, Y axis is the back-calculated HC5s that were generated from SSDs that used the nSpecies
  geom_point(position = position_dodge(width = 0.5))+ # add in the points
  geom_hline(yintercept = Fenthion$Single.C.HC5.bf, colour = "red")+ # Add the "true" HC5 as a red line across
  geom_hline(yintercept = (Fenthion$Single.C.HC5.bf*5), colour = "red", linetype = 2)+ # Add the 5-fold higher mark as a dashed red line
  geom_hline(yintercept = (Fenthion$Single.C.HC5.bf/5), colour = "red", linetype = 2)+ # Add the 5-fold lower mark as a dashed red line
  geom_vline(xintercept = 3.5, linetype = 2)+ # Designate the first quartile to the left of the line
  theme_bw()+ # black and white theme
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+ # rotate x axis labels 45 degrees for reading
  scale_y_log10()+ # make whole graph log scale
  xlab("nSpecies")+
  ylab("HC5 (ug/L)")+
  ggtitle("Fenthion SSDn Estimated HC5s (FISH ONLY)") # add title
Fenthion.plot
```



### Chemical 10: Malathion

#### Plot 1: Raw SSDn Output plot
The chunk below filters the data only for Malathion, then plots the raw output of all the SSDn results. The plot shows that overall, most nSpecies under-estimated the HC5 compared to the "true" HC5.
```{r}
# Filter the data to only include Malathion
Malathion <- Final.Data %>%
  filter(
    Chemical == "Malathion"
  )

# Arrange the nSpecies by the toxicity value (so the most sensitive species are at the top)
Malathion <- Malathion %>%
   arrange(average, nSpecies)

# Extract the order of the species and check
Malathion.n.spec <- unique(Malathion$nSpecies)
Malathion.n.spec

# Relevel the factors to match the order
Malathion$nSpecies <- factor(Malathion$nSpecies, levels = Malathion.n.spec)
       
# Create the plot
Malathion.plot <- ggplot(Malathion, aes(x = nSpecies, y = bf.HC5))+ # X axis is the nSpecies, Y axis is the back-calculated HC5s that were generated from SSDs that used the nSpecies
  geom_point(position = position_dodge(width = 0.5))+ # add in the points
  geom_hline(yintercept = Malathion$Single.C.HC5.bf, colour = "red")+ # Add the "true" HC5 as a red line across
  geom_hline(yintercept = (Malathion$Single.C.HC5.bf*5), colour = "red", linetype = 2)+ # Add the 5-fold higher mark as a dashed red line
  geom_hline(yintercept = (Malathion$Single.C.HC5.bf/5), colour = "red", linetype = 2)+ # Add the 5-fold lower mark as a dashed red line
  geom_vline(xintercept = 3.5, linetype = 2)+ # Designate the first quartile to the left of the line
  theme_bw()+ # black and white theme
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+ # rotate x axis labels 45 degrees for reading
  scale_y_log10()+ # make whole graph log scale
  xlab("nSpecies")+
  ylab("HC5 (ug/L)")+
  ggtitle("Malathion SSDn Estimated HC5s (FISH ONLY)") # add title
Malathion.plot
```



### Chemical 11: Methyl parathion

#### Plot 1: Raw SSDn Output plot
The chunk below filters the data only for Methyl parathion, then plots the raw output of all the SSDn results. The plot shows that overall, most nSpecies under-estimated the HC5 compared to the "true" HC5.
```{r}
# Filter the data to only include Methyl parathion
Methyl.parathion <- Final.Data %>%
  filter(
    Chemical == "Methyl parathion"
  )

# Arrange the nSpecies by the toxicity value (so the most sensitive species are at the top)
Methyl.parathion <- Methyl.parathion %>%
   arrange(average, nSpecies)

# Extract the order of the species and check
Methyl.parathion.n.spec <- unique(Methyl.parathion$nSpecies)
Methyl.parathion.n.spec

# Relevel the factors to match the order
Methyl.parathion$nSpecies <- factor(Methyl.parathion$nSpecies, levels = Methyl.parathion.n.spec)
       
# Create the plot
Methyl.parathion.plot <- ggplot(Methyl.parathion, aes(x = nSpecies, y = bf.HC5))+ # X axis is the nSpecies, Y axis is the back-calculated HC5s that were generated from SSDs that used the nSpecies
  geom_point(position = position_dodge(width = 0.5))+ # add in the points
  geom_hline(yintercept = Methyl.parathion$Single.C.HC5.bf, colour = "red")+ # Add the "true" HC5 as a red line across
  geom_hline(yintercept = (Methyl.parathion$Single.C.HC5.bf*5), colour = "red", linetype = 2)+ # Add the 5-fold higher mark as a dashed red line
  geom_hline(yintercept = (Methyl.parathion$Single.C.HC5.bf/5), colour = "red", linetype = 2)+ # Add the 5-fold lower mark as a dashed red line
  geom_vline(xintercept = 3.5, linetype = 2)+ # Designate the first quartile to the left of the line
  theme_bw()+ # black and white theme
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+ # rotate x axis labels 45 degrees for reading
  scale_y_log10()+ # make whole graph log scale
  xlab("nSpecies")+
  ylab("HC5 (ug/L)")+
  ggtitle("Methyl parathion SSDn Estimated HC5s (FISH ONLY)") # add title
Methyl.parathion.plot
```



### Chemical 12: Parathion

#### Plot 1: Raw SSDn Output plot
The chunk below filters the data only for Parathion, then plots the raw output of all the SSDn results. The plot shows that overall, most nSpecies under-estimated the HC5 compared to the "true" HC5.
```{r}
# Filter the data to only include Parathion
Parathion <- Final.Data %>%
  filter(
    Chemical == "Parathion"
  )

# Arrange the nSpecies by the toxicity value (so the most sensitive species are at the top)
Parathion <- Parathion %>%
   arrange(average, nSpecies)

# Extract the order of the species and check
Parathion.n.spec <- unique(Parathion$nSpecies)
Parathion.n.spec

# Relevel the factors to match the order
Parathion$nSpecies <- factor(Parathion$nSpecies, levels = Parathion.n.spec)
       
# Create the plot
Parathion.plot <- ggplot(Parathion, aes(x = nSpecies, y = bf.HC5))+ # X axis is the nSpecies, Y axis is the back-calculated HC5s that were generated from SSDs that used the nSpecies
  geom_point(position = position_dodge(width = 0.5))+ # add in the points
  geom_hline(yintercept = Parathion$Single.C.HC5.bf, colour = "red")+ # Add the "true" HC5 as a red line across
  geom_hline(yintercept = (Parathion$Single.C.HC5.bf*5), colour = "red", linetype = 2)+ # Add the 5-fold higher mark as a dashed red line
  geom_hline(yintercept = (Parathion$Single.C.HC5.bf/5), colour = "red", linetype = 2)+ # Add the 5-fold lower mark as a dashed red line
  geom_vline(xintercept = 3.5, linetype = 2)+ # Designate the first quartile to the left of the line
  theme_bw()+ # black and white theme
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+ # rotate x axis labels 45 degrees for reading
  scale_y_log10()+ # make whole graph log scale
  xlab("nSpecies")+
  ylab("HC5 (ug/L)")+
  ggtitle("Parathion SSDn Estimated HC5s (FISH ONLY)") # add title
Parathion.plot
```



### Chemical 13: Trichlorfon

#### Plot 1: Raw SSDn Output plot
The chunk below filters the data only for Trichlorfon, then plots the raw output of all the SSDn results. The plot shows that overall, most nSpecies under-estimated the HC5 compared to the "true" HC5.
```{r}
# Filter the data to only include Trichlorfon
Trichlorfon <- Final.Data %>%
  filter(
    Chemical == "Trichlorfon"
  )

# Arrange the nSpecies by the toxicity value (so the most sensitive species are at the top)
Trichlorfon <- Trichlorfon %>%
   arrange(average, nSpecies)

# Extract the order of the species and check
Trichlorfon.n.spec <- unique(Trichlorfon$nSpecies)
Trichlorfon.n.spec

# Relevel the factors to match the order
Trichlorfon$nSpecies <- factor(Trichlorfon$nSpecies, levels = Trichlorfon.n.spec)
       
# Create the plot
Trichlorfon.plot <- ggplot(Trichlorfon, aes(x = nSpecies, y = bf.HC5))+ # X axis is the nSpecies, Y axis is the back-calculated HC5s that were generated from SSDs that used the nSpecies
  geom_point(position = position_dodge(width = 0.5))+ # add in the points
  geom_hline(yintercept = Trichlorfon$Single.C.HC5.bf, colour = "red")+ # Add the "true" HC5 as a red line across
  geom_hline(yintercept = (Trichlorfon$Single.C.HC5.bf*5), colour = "red", linetype = 2)+ # Add the 5-fold higher mark as a dashed red line
  geom_hline(yintercept = (Trichlorfon$Single.C.HC5.bf/5), colour = "red", linetype = 2)+ # Add the 5-fold lower mark as a dashed red line
  geom_vline(xintercept = 3.5, linetype = 2)+ # Designate the first quartile to the left of the line
  theme_bw()+ # black and white theme
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+ # rotate x axis labels 45 degrees for reading
  scale_y_log10()+ # make whole graph log scale
  xlab("nSpecies")+
  ylab("HC5 (ug/L)")+
  ggtitle("Trichlorfon SSDn Estimated HC5s (FISH ONLY)") # add title
Trichlorfon.plot
```

### Combine the results plots and then save
```{r}
# Combine the plots into one
combined.results <- ggarrange(comp.plot.1, comp.plot.2, nrow = 2, ncol = 1, common.legend = TRUE, legend = "right")

# Take a look
combined.results
```

# Save the results plot for the manuscript
```{r}
# save results plot for manuscript as a tiff file
tiff("OP_Fish_Results_FINAL.tiff", units = "in", width = 7.5, height = 10, res = 300) # load an empty tiff file with these dimensions
combined.results # put in the final results plot
dev.off() # close graphics so it saves
```


# Save and export the plots for use in manuscript

### Export SI plots for use in supplemental materials
```{r}
multi.page.plots <- ggarrange(Azinphos.methyl.plot, Chlorpyrifos.plot, Coumaphos.plot, Diazinon.plot, Dichlorvos.plot, Disulfoton.plot, EPN.plot, Fenitrothion.plot, Fenthion.plot, Malathion.plot, Methyl.parathion.plot, Parathion.plot, Trichlorfon.plot, nrow=1, ncol=1) # for one plot per page

multi.page.plots
ggexport(multi.page.plots, filename="OP_Fish_SI_Plots.pdf")
```
